---
title: "Attention EF Paper"
author: "CarterSun"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
```

# - - - - - - - - - - - - - - -

# - PREPARE WORKSPACE ---

# - - - - - - - - - - - - - - -

```{r preparation}
rm(list = ls())
graphics.off()

requiredlibraries <- c("metafor","readxl","RoBMA","TOSTER","dplyr")

# loop over required libraries and install if not present, dependencies might have to be installed manually
for (i in requiredlibraries) {
  if (!(i %in% rownames(installed.packages()))) install.packages(i, dependencies = TRUE)
}
# loop over required libraries to load
for (i in requiredlibraries) {
  current_lib <- i
  if (!i=="meta"){
    library(current_lib, character.only=TRUE)}
}
library(meta)
# library(dmetar)

```

# - - - - - - - - - - - - - - -

# - Load Excel Files ---

# - - - - - - - - - - - - - - -

```{r, results='hide' }

getwd()
setwd('path_to_datafile/')
original_data <- read_excel("Data_Extraction_Form_nesting.xlsx","Data Input New Studies")
# View(original_data)
colnames(original_data) ## get all column names
## Exclude study due to repeat sample across studies
repeat_studies_id_exclude <-c("22","23","24","25","26","99","131","188","268")
original_data <- original_data[!(original_data$`Study No.` %in% repeat_studies_id_exclude), ]

## Exclude study due to not meet inclusion criteria
notmeet_criteria_studies_id_exclude <-c("277","136","254")
original_data <- original_data[!(original_data$`Study No.` %in% notmeet_criteria_studies_id_exclude), ]

# Exclude not 0-5 age
original_data <- original_data[(original_data$`Age group: 0-5 vs. 5-6`== "0-5"), ]

# #separate Clinical Conditions (1-3)
clinicalcondition_1_control <- original_data[,c("Study No." ,"Study_year","Type of Study (Cohort, Cross-sectional, Longitudinal, RCT etc)", "Comparison vs. prediction","Age group: 0-5 vs. 5-6","Age group", "executive function vs. attention","Test Name","Domain (e.g., sustained attention, selective attention, working memory, response inhibition etc)","Outcome variable (subtests/subdomain)","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx1 diagnosis","Main NDDx1 Diagnostic Tool(s)","NDDx1 Mean","NDDx1 Std-Dev","NDDx1 SE","NDDx1 Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx1)","Age NDDx 1 Years (Mean)","Age Control Years (Mean)","Gender (% NDDx1  of Males)","NDDx1 IQ Mean)","NDDx1 IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx1", "NDDx1 diagnosis_code","ToM_code","Domain_code")]
before_exclusion_clinicalcondition_1_control<-clinicalcondition_1_control
remove_patterns <-c('NA','not reported')
clinicalcondition_1_control<-(clinicalcondition_1_control[!grepl(paste(remove_patterns,collapse='|'),clinicalcondition_1_control$`NDDx1 Mean`),])
clinicalcondition_1_control <- clinicalcondition_1_control[!(clinicalcondition_1_control$`NDDx1 Mean` == "" | is.na(clinicalcondition_1_control$`NDDx1 Mean`)), ]

clinicalcondition_2_control <- original_data[,c("Study No." ,"Study_year","Type of Study (Cohort, Cross-sectional, Longitudinal, RCT etc)", "Comparison vs. prediction","Age group: 0-5 vs. 5-6","Age group", "executive function vs. attention","Test Name","Domain (e.g., sustained attention, selective attention, working memory, response inhibition etc)","Outcome variable (subtests/subdomain)","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx2 diagnosis","Main NDDx2 Diagnostic Tool(s)","NDDx2 Mean","NDDx2 Std-Dev","NDDx2 SE","NDDx2 Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx2)","Age NDDx 2 Years (Mean)","Age Control Years (Mean)","Gender (% NDDx2 of Males)","NDDx2 IQ Mean)","NDDx2 IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx2", "NDDx2 diagnosis_code","ToM_code","Domain_code")]
before_exclusion_clinicalcondition_2_control<-clinicalcondition_2_control
clinicalcondition_2_control<-(clinicalcondition_2_control[!grepl(paste(remove_patterns,collapse='|'),clinicalcondition_2_control$`NDDx2 Mean`),])
clinicalcondition_2_control <- clinicalcondition_2_control[!(clinicalcondition_2_control$`NDDx2 Mean` == "" | is.na(clinicalcondition_2_control$`NDDx2 Mean`)), ]


clinicalcondition_3_control <- original_data[,c("Study No.","Study_year","Type of Study (Cohort, Cross-sectional, Longitudinal, RCT etc)","Comparison vs. prediction","Age group: 0-5 vs. 5-6","Age group", "executive function vs. attention","Test Name","Domain (e.g., sustained attention, selective attention, working memory, response inhibition etc)","Outcome variable (subtests/subdomain)","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx3 diagnosis","Main NDDx3 Diagnostic Tool(s)","NDDx3 Mean","NDDx3 Std-Dev","NDDx3 SE","NDDx3 Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx3)","Age NDDx 3 Years (Mean)","Age Control Years (Mean)","Gender (% NDDx3 of Males)","NDDx3 IQ Mean)","NDDx3 IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx3", "NDDx3 diagnosis_code","ToM_code","Domain_code")]
before_exclusion_clinicalcondition_3_control<-clinicalcondition_3_control


clinicalcondition_3_control<-(clinicalcondition_3_control[!grepl(paste(remove_patterns,collapse='|'),clinicalcondition_3_control$`NDDx3 Mean`),])
clinicalcondition_3_control <- clinicalcondition_3_control[!(clinicalcondition_3_control$`NDDx3 Mean` == "" | is.na(clinicalcondition_3_control$`NDDx3 Mean`)), ]


#combine overall conditions
clinicalcondition_1_control_temp = setNames(clinicalcondition_1_control, c("Study No." ,"Study_year","Type of Study", "comparison vs prediction","Age group","Age group broader", "EF_Attention","Test Name","Domain","Outcome variable","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx diagnosis","Main NDDx Diagnostic Tool(s)","NDDx Mean","NDDx Std-Dev","NDDx SE","NDDx Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx)","Age NDDx Years (Mean)","Age Control Years (Mean)","Gender (% NDDx of Males)","NDDx IQ Mean)","NDDx IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx","NDDx_Diagnosis_code","ToM_code","Domain_code"))
clinicalcondition_2_control_temp = setNames(clinicalcondition_2_control, c("Study No." ,"Study_year","Type of Study",  "comparison vs prediction","Age group","Age group broader", "EF_Attention","Test Name","Domain","Outcome variable","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx diagnosis","Main NDDx Diagnostic Tool(s)","NDDx Mean","NDDx Std-Dev","NDDx SE","NDDx Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx)","Age NDDx Years (Mean)","Age Control Years (Mean)","Gender (% NDDx of Males)","NDDx IQ Mean)","NDDx IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx","NDDx_Diagnosis_code","ToM_code","Domain_code"))
clinicalcondition_3_control_temp = setNames(clinicalcondition_3_control, c("Study No." ,"Study_year","Type of Study",  "comparison vs prediction","Age group","Age group broader", "EF_Attention","Test Name","Domain","Outcome variable","Accuracy/Response time (ms)/Behav rating/physiological/preference","Type of measure (i.e., biological, behavioural, rating form)", "NDDx diagnosis","Main NDDx Diagnostic Tool(s)","NDDx Mean","NDDx Std-Dev","NDDx SE","NDDx Sample size","Control Mean","Control Std-Dev","Control SE","Control Sample size","Effect direction (NDDx)","Age NDDx Years (Mean)","Age Control Years (Mean)","Gender (% NDDx of Males)","NDDx IQ Mean)","NDDx IQ (SD)","Control IQ (Mean)","Control IQ (SD)","IQ Type","IQ test","Comparison Group","Gender","Assessment Tool Type (psychometric, experimental, questionnaire, interview)","Assesment Tool Administration Format","Mode of Assessment","Stimulus Presentation Format","Participant Processing Mode","Participant Response Mode","IQ Difference Significant","Language age Difference Significant","Matching Variable", "DSM/ICD edition NDDx","NDDx_Diagnosis_code","ToM_code","Domain_code"))
All_clinicalcondition_with_control <- Reduce(function(x, y) merge(x, y, all=TRUE),
                                               list(clinicalcondition_1_control_temp, clinicalcondition_2_control_temp, clinicalcondition_3_control_temp))
All_clinicalcondition_with_control[complete.cases(All_clinicalcondition_with_control), ] #remove missing values
rm(clinicalcondition_1_control_temp,clinicalcondition_2_control_temp,clinicalcondition_3_control_temp)
# View(All_clinicalcondition_with_control)
# writexl::write_xlsx(All_clinicalcondition_with_control,"cleanedtable_all_clinicalcondition_with_control_just_removed_outliers.xlsx", col_names = TRUE)

cross_sectional <-All_clinicalcondition_with_control %>% filter(All_clinicalcondition_with_control$`comparison vs prediction`=="c")


# writexl::write_xlsx(cross_sectional,"cleanedtable_clinicalcondition_with_control_crosssectional_only_just_removed_outliers.xlsx", col_names = TRUE)
notcross_sectional <-All_clinicalcondition_with_control %>% filter(All_clinicalcondition_with_control$`comparison vs prediction`!="c")

# writexl::write_xlsx(notcross_sectional,"cleanedtable_clinicalcondition_with_control_not_crosssectional_just_removed_outliers.xlsx", col_names = TRUE)


```

# --

# NDDx Effect Size Calculation

# --

# SE to STD Function

```{r}
convert_se_to_std <- function(se,n){
  if (is.na(se) || se =="Not Reported" || se == "NA"){
    return(se)
  } else {
      return(se*sqrt(n))
  }
}
```

# Cohen's d to Hedge's g Conversion
```{r}
hedges_g <- function(d, totaln) {
  correction_factor <- 1 - (3 / (4 * totaln - 9))
  g <- d * correction_factor
  return(g)
}
```

# I-squared calculation Function

```{r}
I_squared <- function(tau2_value, sigma2_value){
  score <-sqrt(tau2_value / (tau2_value + sigma2_value)) *100
  output<-sprintf("%.2f%%",score)
  return( output)

}
```
# p-value reformatting

```{r}

p_value <- function(pooled_pval){
  p_value <- ifelse(
                    pooled_pval < 0.001,"<0.001", sprintf("%.3f", pooled_pval)
  )
  return (p_value)
}

```
# Define All Types of Labels Here for Forest Plots

```{r}
### Numeric to String Label (Age group)
age_definitions <-c("Infants","Toddlers","Preschool")
age_string <-function(age_int){
  if (age_int >= 1 && age_int <= length(age_definitions)) {
      return(age_definitions[age_int])
  } else {
      return("Unknown Age Group")
  }
}

### Numeric to String Label (Domain Labels)
domain_definitions <- c(
  "Complex Working Memory", "Simple Response Inhibition",
  "Complex Response Inhibition", "Response Shifting", "Attention Shifting",
  "Higher-order EF", "Inhibit/Impulsivity/Inhibitory Control", "Shift", "Emotional Control",
  "Working Memory", "Plan/Organize", "Inhibitory Self-control", "Flexibility",
  "Emergent Metacognition", "Global Executive Function/Effortful Control","Simple Working Memory"
)
domain_string <-function(domain_int){
  if (domain_int >= 1 && domain_int <= length(domain_definitions)) {
    return(domain_definitions[domain_int])
  } else {
    return("Unknown Domain Group")
  }
}

### Numeric to String Label (NDDx Diagnisis Code Labels)
NDDX_definitions <- c(
  "IDD", "Communication Disorders","ASD","ADHD","Specific Learning Disorder",
  "Motor Disorders","Genetic Disorders","FASD","Cerebral Palsy","Comorbid NDDs","High-risk ASD","Mixed NDDs",
  "Comorbid NDD + non-NDD","High-risk ADHD","High-risk Communication Disorder","High-risk ASD + High-risk ADHD","High-risk FASD"
)
NDDx_string <-function(nddxcode_int){
  if (nddxcode_int >= 1 && nddxcode_int <= length(NDDX_definitions)) {
    return(NDDX_definitions[nddxcode_int])
  } else {
    return("Unknown NDDx Group")
  }
}
```
## Step 0: remove row if std/sample size is not reported

```{r}
# Remove rows with both "Not Reported" or "NA" values in std and se columns
filtered_All_clinicalcondition_cross_sectionalonly <- cross_sectional[!((cross_sectional$`NDDx Std-Dev`== "Not Reported" & cross_sectional$`NDDx SE` == "Not Reported") | (is.na(cross_sectional$`NDDx Std-Dev`) & is.na(cross_sectional$`NDDx SE`))), ]

filtered_All_clinicalcondition_with_control_cross_sectionalonly <- filtered_All_clinicalcondition_cross_sectionalonly[!((filtered_All_clinicalcondition_cross_sectionalonly$`Control Std-Dev`== "Not Reported" & filtered_All_clinicalcondition_cross_sectionalonly$`Control SE` == "Not Reported") |( is.na(filtered_All_clinicalcondition_cross_sectionalonly$`Control Std-Dev`) & is.na(filtered_All_clinicalcondition_cross_sectionalonly$`Control SE`))), ]


checking_columns <- c("NDDx Mean", "NDDx Std-Dev", "NDDx Sample size","Control Mean","Control Std-Dev","Control Sample size")
missing_std_NDDx <-is.na(filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx Std-Dev`) | filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx Std-Dev` == "Not Reported" | filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx Std-Dev` == "NA"

# ## convert string to numeric format
# 
i<-c(15:30)
filtered_All_clinicalcondition_with_control_cross_sectionalonly[,i]<-apply(filtered_All_clinicalcondition_with_control_cross_sectionalonly[,i],2,function(x) as.numeric(as.character(x)))
i<-c(45:47)
filtered_All_clinicalcondition_with_control_cross_sectionalonly[,i]<-apply(filtered_All_clinicalcondition_with_control_cross_sectionalonly[,i],2,function(x) as.numeric(as.character(x)))

# View(filtered_All_clinicalcondition_with_control_cross_sectionalonly)
## convert se to std if std was not originally reported
filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx Std-Dev`[missing_std_NDDx] <- mapply(convert_se_to_std, filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx SE`[missing_std_NDDx], filtered_All_clinicalcondition_with_control_cross_sectionalonly$`NDDx Sample size`[missing_std_NDDx])

missing_std_control <-is.na(filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control Std-Dev`) | filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control Std-Dev` == "Not Reported" | filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control Std-Dev` == "NA"

filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control Std-Dev`[missing_std_control] <- mapply(convert_se_to_std,filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control SE`[missing_std_control], filtered_All_clinicalcondition_with_control_cross_sectionalonly$`Control Sample size`[missing_std_control])


filtered_all_NDDx_control <- filtered_All_clinicalcondition_with_control_cross_sectionalonly[!(rowSums(is.na(filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns]) | filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns] == "Not reported" | filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns] == "NA") > 0), ]

missing_afterconversion_all_NDDx_control <- filtered_All_clinicalcondition_with_control_cross_sectionalonly[(rowSums(is.na(filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns]) | filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns] == "Not reported" | filtered_All_clinicalcondition_with_control_cross_sectionalonly[checking_columns] == "NA") > 0), ]

# View(missing_afterconversion_all_NDDx_control)
```
## Step 1: Calculate effect sizes of cross-sectional studies and split data for analysis
### Note: All changes made were saved in an excel file for cross-checking

```{r, results='hide'}
NDDx_control_EffectSize<- escalc(measure="SMD", m1i=filtered_all_NDDx_control$`NDDx Mean`, sd1i=filtered_all_NDDx_control$`NDDx Std-Dev`, n1i=filtered_all_NDDx_control$`NDDx Sample size`, m2i=filtered_all_NDDx_control$`Control Mean`,sd2i=filtered_all_NDDx_control$`Control Std-Dev`,n2i=filtered_all_NDDx_control$`Control Sample size`,
                                        slab=paste(filtered_all_NDDx_control$`Study No.`,sep=""))
new_yi <- NDDx_control_EffectSize$yi


for (i in 1:length(new_yi)){
  if(filtered_all_NDDx_control$`Effect direction (NDDx)`[i] == 1 && new_yi[i] < 0){
    new_yi[i] = -new_yi[i]
  } else if(filtered_all_NDDx_control$`Effect direction (NDDx)`[i] == 2 && new_yi[i] > 0){
    new_yi[i] = -new_yi[i]
  } #else keep new_yi unchanged (1 - positive, 2- negative, 3- no mean differences)
}
filtered_all_NDDx_control$yi <- new_yi
filtered_all_NDDx_control$vi <-NDDx_control_EffectSize$vi


NDDx_summary <- escalc(yi=yi,vi=vi,data=filtered_all_NDDx_control)
# View(NDDx_summary)

# writexl::write_xlsx(NDDx_summary,"NDDx_control_effectsizes_just_removed_outliers.xlsx",col_names=TRUE)

NDDx_summary_ef <-NDDx_summary%>% filter(NDDx_summary$EF_Attention == "executive function")

## level 1 (sub-scales are not included for the overall study effects)

ef_level1<-c("global executive function","effortful control")
# NDDx_summary_ef_behaviour_biological_global_effortforcontrol <- NDDx_summary_ef[(NDDx_summary_ef$`Domain (e.g., sustained attention, selective attention, working memory, response inhibition etc)` %in% ef_level1), ] 

# Behavioural is study all to be included, for rating form (only global executive function and eefortful control are included in all future analysis) -EF studies
strings_to_match <- c( "behavioural","Behavioural")
strings_rf <- c( "rating form")

NDDx_summary_ef_only_behavioural <- NDDx_summary_ef[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary_ef$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE), ]

NDDx_summary_ef_level1_and_behaviour <- NDDx_summary_ef[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary_ef$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE) |
  NDDx_summary_ef$`Domain` %in% ef_level1,]

NDDx_summary_ef_level1_and_behaviour_attention_combined <- NDDx_summary[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE) |
  NDDx_summary$`Domain` %in% ef_level1,]
#level 2 means all subscales (not global and effortforcontrol) in rating form only EF Studies
# NDDx_summary_ef_exclude_global_effortforcontrol <- NDDx_summary_ef_ratingform[!(NDDx_summary_ef_ratingform$`Domain` %in% ef_level1), ] 


NDDx_summary_ef_ratingform<-NDDx_summary_ef[(NDDx_summary_ef$`Type.of.measure..i.e...biological..behavioural..rating.form.` %in% strings_rf),]
NDDx_summary_ef_ratingform_level1<-NDDx_summary_ef_level1_and_behaviour[(NDDx_summary_ef_level1_and_behaviour$`Type.of.measure..i.e...biological..behavioural..rating.form.` %in% strings_rf),]

NDDx_summary_ef_level2 <- NDDx_summary_ef_ratingform[!(NDDx_summary_ef_ratingform$`Domain` %in% ef_level1),]

domain_subscales <-c(7,8,9,10,11)
NDDx_summary_ef_ratingform_subscales <-  NDDx_summary_ef_ratingform[NDDx_summary_ef_ratingform$Domain_code %in% domain_subscales, ] # domains 7-11
domain_factors <-c(12,13,14)
NDDx_summary_ef_ratingform_factors <-  NDDx_summary_ef_ratingform[NDDx_summary_ef_ratingform$Domain_code %in% domain_factors, ] # domains 7-11


NDDx_summary_attention <-NDDx_summary%>% filter(NDDx_summary$EF_Attention == "attention")
# writexl::write_xlsx(NDDx_summary_ef,"NDDx_control_effectsizes_executivefunction_just_removed_outliers.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_level1_and_behaviour,"NDDx_control_effectsizes_executivefunction_global_effortfor_behavioural_finalforpublication.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_level2,"NDDx_control_effectsizes_executivefunction_subscales_inratingform_just_removed_outliers.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_attention,"NDDx_control_effectsizes_attention_finalforpublication.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_only_behavioural,"NDDx_control_effectsizes_onlybehaviour_just_removed_outliers.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_ratingform_level1,"NDDx_control_effectsizes_onlyrf_level1_just_removed_outliers.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_level1_and_behaviour_attention_combined,"NDDx_control_effectsizes_attention_and_ef_level1_just_removed_outliers.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_ratingform_subscales,"NDDx_control_effectsizes_ef_ratingform_subscales_just_removed_outliers.xlsx",col_names=TRUE)
# writexl::write_xlsx(NDDx_summary_ef_ratingform_factors,"NDDx_control_effectsizes_ef_ratingform_factors_just_removed_outliers.xlsx",col_names=TRUE)

# View(NDDx_summary_ef)
# NDDx_summary_ef[, 1] <- as.numeric(as.character(NDDx_summary_ef[, 1]))
# NDDx_summary_ef[, 6] <- as.numeric(as.character(NDDx_summary_ef[, 6]))
NDDx_summary_ef_level1_and_behaviour[, 1] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour[, 1]))
NDDx_summary_ef_level1_and_behaviour[, 6] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour[, 6]))
NDDx_summary_ef_ratingform_level1[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_level1[, 1]))
NDDx_summary_ef_ratingform_level1[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_level1[, 6]))
NDDx_summary_ef_level2[, 1] <- as.numeric(as.character(NDDx_summary_ef_level2[, 1]))
NDDx_summary_ef_level2[, 6] <- as.numeric(as.character(NDDx_summary_ef_level2[, 6]))
# View(NDDx_summary_attention)
NDDx_summary_attention[, 1] <- as.numeric(as.character(NDDx_summary_attention[, 1]))
NDDx_summary_attention[, 6] <- as.numeric(as.character(NDDx_summary_attention[, 6]))
NDDx_summary_ef_only_behavioural[, 1] <- as.numeric(as.character(NDDx_summary_ef_only_behavioural[, 1]))
NDDx_summary_ef_only_behavioural[, 6] <- as.numeric(as.character(NDDx_summary_ef_only_behavioural[, 6]))
NDDx_summary_ef_level1_and_behaviour_attention_combined[, 1] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour_attention_combined[, 1]))
NDDx_summary_ef_level1_and_behaviour_attention_combined[, 6] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour_attention_combined[, 6]))
NDDx_summary_ef_ratingform_subscales[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_subscales[, 1]))
NDDx_summary_ef_ratingform_subscales[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_subscales[, 6]))
NDDx_summary_ef_ratingform_factors[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_factors[, 1]))
NDDx_summary_ef_ratingform_factors[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_factors[, 6]))

```

#---------------------
# -- Original Data Analysis
#---------------------
## Step 2.0 Overall Estimates Per study in each attention/EF level 1 +behaviour

```{r}
# Assuming you have a dataframe named filtered_all_NDDx_control
# with columns study_ID, ef_attention, yi, and vi

# Get unique combinations of study_ID and ef_attention
unique_combinations <- unique(NDDx_summary[, c("Study.No.", "EF_Attention")])

# Initialize an empty list to store the results
results <- c()
# Loop through each combination
for (i in 1:nrow(unique_combinations)) {
  current_combination <- unique_combinations[i, ]
  
  # Filter the data for the current combination
  current_data <- NDDx_summary %>%
    filter(Study.No. == current_combination$`Study.No.`, EF_Attention == current_combination$`EF_Attention`)
  
  # Calculate the mean yi and vi for the current combination
  mean_yi <- mean(current_data$yi)
  mean_vi <- mean(current_data$vi)
  mean_SE <- sqrt(mean_vi)
  # Add the results to the list
  results[[i]] <- list(
    Study_No= current_combination$`Study.No.`,
    EF_Attention = current_combination$`EF_Attention`,
    mean_yi = mean_yi,
    mean_vi = mean_vi,
    mean_se = mean_SE
  )
}

# Convert the list of results to a dataframe
estimates_perstudy <- as.data.frame(do.call(rbind, results))
View(estimates_perstudy)

# Print the overall yi and vi values along with study_ID and ef_attention
# library(xlsx)
writexl::write_xlsx(estimates_perstudy,"overall_yi_vi_forpublication_original.xlsx")

```

## Step 2.1: overall random effect (EF level 1 and behaviour)

```{r}
# Multi-variant random effect (across studies) executive 
current<-list()
random_effect_study_ef_level1 <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(random_effect_study_ef_level1, digits=3)
predict(random_effect_study_ef_level1)
pooled_effect <- random_effect_study_ef_level1$b
pooled_effect_ci_lb <- random_effect_study_ef_level1$ci.lb
pooled_effect_ci_ub <- random_effect_study_ef_level1$ci.ub
  
pooled_effect_nlevel <-random_effect_study_ef_level1$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_ef_level1$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_ef_level1$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_ef_level1$tau2, random_effect_study_ef_level1$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_ef_level1$pval)
pooled_qe <-random_effect_study_ef_level1$QE
pooled_qedf <-random_effect_study_ef_level1$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_ef_level1$QEp)
pooled_qm <-random_effect_study_ef_level1$QM
pooled_qmdf <-random_effect_study_ef_level1$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_ef_level1$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  # Pooled_sigma2= unlist(pooled_effect_sigma2),
  
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
# forest(random_effect_study_ef_level1)

writexl::write_xlsx(current,"pooled_overall_ef_level1_behaviour_original.xlsx",col_names=TRUE)
```
### Step 2.1.1: Funnel plot and trim-and-fill analysis (EF level 1 and behaviour)
```{r}
NDDx_summary_ef_level1_and_behaviour$SE<-sqrt(NDDx_summary_ef_level1_and_behaviour$vi)
Data_meta_means_NDDx_summary_ef_level1_and_behaviour <-
  NDDx_summary_ef_level1_and_behaviour %>% select(`Study.No.`, `Domain`, yi, SE, vi) %>%
  group_by(`Study.No.`,) %>%
  summarise(mean_g=mean(yi),mean_SE=mean(SE), mean_Vi=mean(vi))

eggers_EF <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$`Study.No.`,sep=""))
## Uni-variant 
random_effect_study_ef_level1_and_behaviour_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_ef_level1_and_behaviour) 
print(random_effect_study_ef_level1_and_behaviour_univariant,digits=3)
predict(random_effect_study_ef_level1_and_behaviour_univariant)
funnel(random_effect_study_ef_level1_and_behaviour_univariant)

taf_ef_level1 <- trimfill(random_effect_study_ef_level1_and_behaviour_univariant, side = "left")
funnel_figure4b<-recordPlot({
  funnel(taf_ef_level1,legend=TRUE,main="Executive Function\n(before removal of outliers)", cex.main = 0.7, cex.lab = 0.7, cex.axis = 0.7)
})
```

## Step 2.2: overall random effect (Attention)

```{r}
#Multi-variant random effect (across studies) attention
current<-list()
NDDx_summary_attention <- NDDx_summary_attention[order(NDDx_summary_attention$yi), ]

random_effect_study_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$Study.No.,sep=""))
summary(random_effect_study_attention, digits=3)
predict(random_effect_study_attention)
pooled_effect <- random_effect_study_attention$b
pooled_effect_ci_lb <- random_effect_study_attention$ci.lb
pooled_effect_ci_ub <- random_effect_study_attention$ci.ub
  
pooled_effect_nlevel <-random_effect_study_attention$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_attention$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_attention$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_attention$tau2, random_effect_study_attention$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_attention$pval)
pooled_qe <-random_effect_study_attention$QE
pooled_qedf <-random_effect_study_attention$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_attention$QEp)
pooled_qm <-random_effect_study_attention$QM
pooled_qmdf <-random_effect_study_attention$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_attention$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
meta::forest(random_effect_study_attention)
writexl::write_xlsx(current,"pooled_overall_attention_original.xlsx",col_names=TRUE)
```

### Step 2.2.1: Funnel plot and trim-and-fill analysis (Attention)
```{r}
NDDx_summary_attention$SE<-sqrt(NDDx_summary_attention$vi)
Data_meta_means_NDDx_summary_attention <-
  NDDx_summary_attention %>% select(`Study.No.`, `Domain`, yi, SE, vi) %>%
  group_by(`Study.No.`,) %>%
  summarise(mean_g=mean(yi),mean_SE=mean(SE), mean_Vi=mean(vi))

eggers_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$`Study.No.`,sep=""))
## Uni-variant 
random_effect_study_attention_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_attention) 
print(random_effect_study_attention_univariant,digits=3)
predict(random_effect_study_attention_univariant)
funnel(random_effect_study_attention_univariant)
```
# Additional Bayesian Model
```{r}
# library(RoBMA)
# robustbayesian_ef_level1<-RoBMA(d= NDDx_summary_ef_level1_and_behaviour$yi, v=NDDx_summary_ef_level1_and_behaviour$vi, study_ids =NDDx_summary_ef_level1_and_behaviour$`Study.No.`,priors_bias = NULL,parallel = TRUE, seed = 1)
# summary(robustbayesian_ef_level1)
# 
# robustbayesian_attention<-RoBMA(d= NDDx_summary_attention$yi, v=NDDx_summary_attention$vi, study_ids =NDDx_summary_attention$`Study.No.`,priors_bias = NULL,parallel = TRUE, seed = 1)
# summary(robustbayesian_attention)
```
#------------------------------
# - After removing outliers
#------------------------------

# Removing studys that has g>2
```{r}
# remove study no with g>2
## EF
ef_toremove <- c(237, 110,264,106)
attention_toremove <- c(157, 120,189)

NDDx_summary_ef_level1_and_behaviour<-NDDx_summary_ef_level1_and_behaviour[!(NDDx_summary_ef_level1_and_behaviour$Study.No.%in% ef_toremove),]
Data_meta_means_NDDx_summary_ef_level1_and_behaviour<-Data_meta_means_NDDx_summary_ef_level1_and_behaviour[!(Data_meta_means_NDDx_summary_ef_level1_and_behaviour$Study.No.%in% ef_toremove),]

## Attention
NDDx_summary_attention<-NDDx_summary_attention[!(NDDx_summary_attention$Study.No. %in% attention_toremove),]
Data_meta_means_NDDx_summary_attention<-Data_meta_means_NDDx_summary_attention[!(Data_meta_means_NDDx_summary_attention$Study.No.%in% attention_toremove),]


## Funnel plot after removing mean_g>2
### Step 1: EF level 1
eggers_EF_outlierremoved <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$`Study.No.`,sep=""))
#### Uni-variant 
random_effect_study_ef_level1_and_behaviour_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_ef_level1_and_behaviour) 
print(random_effect_study_ef_level1_and_behaviour_univariant,digits=3)
predict(random_effect_study_ef_level1_and_behaviour_univariant)
funnel(random_effect_study_ef_level1_and_behaviour_univariant)

taf_ef_level1_outlierremoved <- trimfill(random_effect_study_ef_level1_and_behaviour_univariant, side = "left")


### Step 2: Attention
eggers_attention_outlierremoved <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$`Study.No.`,sep=""))
## Uni-variant 
random_effect_study_attention_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_attention) 
print(random_effect_study_attention_univariant,digits=3)
predict(random_effect_study_attention_univariant)
funnel(random_effect_study_attention_univariant)


taf_attention_outlierremoved<- trimfill(random_effect_study_attention_univariant, side = "left")
```
## Plotting Funnel plots (Figure 4)
```{r}
# Convert dimensions from millimeters to inches
width_mm <- 180  # width in millimeters
height_mm <- 200 # height in millimeters

width_in <- width_mm / 25.4  # Convert to inches
height_in <- height_mm / 25.4 # Convert to inches

svg("funnel_plots_Figure4.svg", width = width_in, height = height_in, pointsize = 7)

par(mfrow = c(2, 2),              
    mar = c(5, 4, 4, 2) + 0.1,    
    oma = c(3, 1, 3, 1),           
    family = "Helvetica",
    fontsize=0.7, cex = 0.7, cex.lab = 0.7, cex.axis = 0.7, cex.main = 0.7)

funnel(taf_attention,legend=TRUE,main="Attention\n(before removal of outliers)", cex.main = 0.7, cex.lab = 0.7, cex.axis = 0.7)
mtext("(A)", side = 1, line = 5, at = mean(par("usr")[1:2]),cex = 0.7)
funnel(taf_ef_level1,legend=TRUE,main="Executive Function\n(before removal of outliers)", cex.main = 0.7, cex.lab = 0.7, cex.axis = 0.7)
mtext("(B)", side = 1, line = 5, at = mean(par("usr")[1:2]), cex = 0.7)
funnel(taf_attention_outlierremoved,legend=TRUE,main="Attention\n(after removal of outliers)", cex.main = 0.7, cex.lab = 0.7, cex.axis = 0.7)
mtext("(C)", side = 1, line = 5, at = mean(par("usr")[1:2]),cex = 0.7)
funnel(taf_ef_level1_outlierremoved,legend=TRUE,main="Executive Function\n(after removal of outliers)", cex.main = 0.7, cex.lab = 0.7, cex.axis = 0.7)
mtext("(D)", side = 1, line = 5, at = mean(par("usr")[1:2]), cex = 0.7)

```

## Step 2.1: overall random effect (EF level 1 and behaviour)

```{r}
# Multi-variant random effect (across studies) executive 
current<-list()
NDDx_summary_ef_level1_and_behaviour <- NDDx_summary_ef_level1_and_behaviour[order(NDDx_summary_ef_level1_and_behaviour$yi), ]

random_effect_study_ef_level1 <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(random_effect_study_ef_level1, digits=3)
predict(random_effect_study_ef_level1)
pooled_effect <- random_effect_study_ef_level1$b
pooled_effect_ci_lb <- random_effect_study_ef_level1$ci.lb
pooled_effect_ci_ub <- random_effect_study_ef_level1$ci.ub
  
pooled_effect_nlevel <-random_effect_study_ef_level1$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_ef_level1$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_ef_level1$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_ef_level1$tau2, random_effect_study_ef_level1$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_ef_level1$pval)
pooled_qe <-random_effect_study_ef_level1$QE
pooled_qedf <-random_effect_study_ef_level1$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_ef_level1$QEp)
pooled_qm <-random_effect_study_ef_level1$QM
pooled_qmdf <-random_effect_study_ef_level1$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_ef_level1$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
forest(random_effect_study_ef_level1, cex = 0.8,width=10)
writexl::write_xlsx(current,"pooled_overall_ef_level1_behaviour_just_removed_outliers.xlsx",col_names=TRUE)
```
## Step 2.2: overall random effect (Attention)

```{r}
#Multi-variant random effect (across studies) attention
current<-list()
NDDx_summary_attention <- NDDx_summary_attention[order(NDDx_summary_attention$yi), ]

random_effect_study_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$Study.No.,sep=""))
summary(random_effect_study_attention, digits=3)
predict(random_effect_study_attention)
pooled_effect <- random_effect_study_attention$b
pooled_effect_ci_lb <- random_effect_study_attention$ci.lb
pooled_effect_ci_ub <- random_effect_study_attention$ci.ub
  
pooled_effect_nlevel <-random_effect_study_attention$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_attention$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_attention$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_attention$tau2, random_effect_study_attention$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_attention$pval)
pooled_qe <-random_effect_study_attention$QE
pooled_qedf <-random_effect_study_attention$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_attention$QEp)
pooled_qm <-random_effect_study_attention$QM
pooled_qmdf <-random_effect_study_attention$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_attention$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
forest(random_effect_study_attention, cex = 0.8,width=10)

writexl::write_xlsx(current,"pooled_overall_attention_just_removed_outliers.xlsx",col_names=TRUE)
```

# Additional Hirerarchical Bayesian Model-Averaged Meta-Analysis

```{r}
# library(RoBMA)
robustbayesian_ef_level1<-RoBMA(d= NDDx_summary_ef_level1_and_behaviour$yi, v=NDDx_summary_ef_level1_and_behaviour$vi, study_ids =NDDx_summary_ef_level1_and_behaviour$`Study.No.`,priors_bias = NULL,parallel = TRUE, seed = 1)
summary(robustbayesian_ef_level1)
interpret(robustbayesian_ef_level1, output_scale = NULL)

robustbayesian_attention<-RoBMA(d= NDDx_summary_attention$yi, v=NDDx_summary_attention$vi, study_ids =NDDx_summary_attention$`Study.No.`,priors_bias = NULL,parallel = TRUE, seed = 1)
summary(robustbayesian_attention)
interpret(robustbayesian_attention, output_scale = NULL)
```



# Attention multi-variate effect

## Overall Attention Effect per type of measure

```{r}
skipped_attentionmeasure_lessstudyonly <-c()
attention_typeofmeasures<-c()
attention_tom_pooled_ef <- list()
attention_tom_pooled_ci_lb <- list()
attention_tom_pooled_ci_ub <- list()
attention_tom_pooled_p<- list()
attention_tom_pooled_k<-list()
attention_tom_pooled_nlevel<- list()
for (tom_label in unique(NDDx_summary_attention$Type.of.measure..i.e...biological..behavioural..rating.form.)){
  each_type_of_measure_dataset <- c()
  each_type_of_measure_dataset <-NDDx_summary_attention %>% filter(NDDx_summary_attention$Type.of.measure..i.e...biological..behavioural..rating.form.== tom_label )
  # print(tom_label)
 if(length(unique(each_type_of_measure_dataset$Study.No.)) <=2){
    skipped_attentionmeasure_lessstudyonly<-c(skipped_attentionmeasure_lessstudyonly, tom_label)
    next
  }
  #print(each_type_of_measure_dataset)
  attention_typeofmeasures[[tom_label]] <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=each_type_of_measure_dataset, slab=paste(each_type_of_measure_dataset$Study_year,sep=""))

  #print(attention_typeofmeasures[[tom_label]], digits=3)
  forest_plot_attention_typeofmeasure<-metafor::forest(attention_typeofmeasures[[tom_label]],addpred=TRUE,header=TRUE)
  # print(forest_plot_attention_typeofmeasure, digits = 3)
  text(x = 0, y = nrow(each_type_of_measure_dataset) + 1, labels = tom_label, pos = 3)
  
  # Extract pooled effect size from each domain_label
  attention_tom_pooled_ef[[tom_label]] <- attention_typeofmeasures[[tom_label]]$b
  attention_tom_pooled_ci_lb[[tom_label]] <- attention_typeofmeasures[[tom_label]]$ci.lb
  attention_tom_pooled_ci_ub[[tom_label]] <- attention_typeofmeasures[[tom_label]]$ci.ub
  attention_tom_pooled_p[[tom_label]] <- attention_typeofmeasures[[tom_label]]$pval
  attention_tom_pooled_k[[tom_label]] <- attention_typeofmeasures[[tom_label]]$k
  attention_tom_pooled_nlevel[[tom_label]] <- attention_typeofmeasures[[tom_label]]$s.nlevels

  
}

# Create a data frame of pooled effects
pooled_effects_tom_attention_dataframe <- data.frame(
  TOM = names(attention_tom_pooled_ef),
  Pooled_Effect = unlist(attention_tom_pooled_ef),
  Pooled_cilb = unlist(attention_tom_pooled_ci_lb),
  Pooled_ciub  = unlist(attention_tom_pooled_ci_ub),
  Pooled__p  = unlist(attention_tom_pooled_p),
  Pooled_k  = unlist(attention_tom_pooled_k),
  Pooled_nlevel  = unlist(attention_tom_pooled_nlevel)

)
# Create a single forest plot to display the pooled effects of sub-domains
overall_forest_plot_tom_attention <- metafor::forest(pooled_effects_tom_attention_dataframe$Pooled_Effect, 
                                       ci.lb = pooled_effects_tom_attention_dataframe$Pooled_cilb, 
                                       ci.ub = pooled_effects_tom_attention_dataframe$Pooled_ciub,
                                       slab = paste(pooled_effects_tom_attention_dataframe$TOM),
                                       xlim = c(-5, 5),  # Adjust as needed
                                       addsummary = TRUE,
                                       addpred=TRUE, 
                                       header = "Type of Measures",
                                       xlab = "Hedges' g",

                                       digits = 3)


cat("less than three studies, not suitable for meta-analysis:", paste(skipped_attentionmeasure_lessstudyonly, collapse = ", "),"\n")
skipped_datasets_attention <- NDDx_summary_attention[NDDx_summary_attention$Type.of.measure..i.e...biological..behavioural..rating.form. %in% skipped_attentionmeasure_lessstudyonly, ]
# View(skipped_datasets_attention)
# writexl::write_xlsx(skipped_datasets_attention,"NDDx_control_effectsizes_Attention_skippedstudies_just_removed_outliers.xlsx",col_names=TRUE)
# writexl::write_xlsx(pooled_effects_tom_attention_dataframe,"pooled_effects_tom_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```

# Overall EF Effect per Domain

## Step 1 Level 1 and behaviour EF per domain

```{r}

skipped_level1_domains_lessstudyonly <-c()

EF_perdomain_level1<-c()

EF_perdomain_level1_no_rf_pooled_ef <- list()

EF_perdomain_level1_no_rf_pooled_ci_lb <- list()

EF_perdomain_level1_no_rf_pooled_ci_ub <- list()
EF_perdomain_level1_no_rf_nlevel<- list()
EF_perdomain_level1_no_rf_I_sqr<- list()
EF_perdomain_level1_no_rf_p<- list()
EF_perdomain_level1_no_rf_k<- list()
EF_perdomain_level1_no_rf_tau2<- list()
EF_perdomain_level1_no_rf_qe<- list()
EF_perdomain_level1_no_rf_qe_df<- list()
EF_perdomain_level1_rf_qe_p<- list()
EF_perdomain_level1_rf_qm<- list()
EF_perdomain_level1_rf_qm_df<- list()
EF_perdomain_level1_rf_qm_p<- list()
EF_perdomain_level1_rf_sigma2<- list()
for (domain_label in unique(NDDx_summary_ef_level1_and_behaviour$`Domain`)){

  each_level1_ef_domain_dataset <- c()

  each_level1_ef_domain_dataset <-NDDx_summary_ef_level1_and_behaviour%>% filter(NDDx_summary_ef_level1_and_behaviour$`Domain`== domain_label)

  # print(domain_label)

  if(length(unique(each_level1_ef_domain_dataset$Study.No.)) <=2){

    skipped_level1_domains_lessstudyonly<-c(skipped_level1_domains_lessstudyonly, domain_label)

    next

  }
  each_level1_ef_domain_dataset <- each_level1_ef_domain_dataset[order(each_level1_ef_domain_dataset$yi), ]

  EF_perdomain_level1[[domain_label]] <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=each_level1_ef_domain_dataset, slab=paste(each_level1_ef_domain_dataset$Study_year,sep=""))

  print(EF_perdomain_level1[[domain_label]], digits=3)

  forest_plot_efdomain_level1<-metafor::forest(EF_perdomain_level1[[domain_label]],addpred=TRUE,header=TRUE)

  text(x = 0, y = nrow(each_level1_ef_domain_dataset) + 1, labels = domain_label, pos = 3)

  print(forest_plot_efdomain_level1, digits = 3)

  # Extract pooled effect size from each domain_label

  pooled_effect <- EF_perdomain_level1[[domain_label]]$b

  pooled_effect_ci_lb <- EF_perdomain_level1[[domain_label]]$ci.lb

  pooled_effect_ci_ub <- EF_perdomain_level1[[domain_label]]$ci.ub

  EF_perdomain_level1_no_rf_pooled_ef[[domain_label]]<-pooled_effect

  EF_perdomain_level1_no_rf_pooled_ci_lb[[domain_label]]<-pooled_effect_ci_lb

  EF_perdomain_level1_no_rf_pooled_ci_ub[[domain_label]]<-pooled_effect_ci_ub

  pooled_effect_nlevel <-EF_perdomain_level1[[domain_label]]$s.nlevels # number of studies
  pooled_effect_k <-EF_perdomain_level1[[domain_label]]$k.eff # number of outcomes
  pooled_effect_tau2 <-EF_perdomain_level1[[domain_label]]$tau2
  pooled_effect_sigma2 <-EF_perdomain_level1[[domain_label]]$sigma2
  pooled_I2 <- mapply(I_squared,EF_perdomain_level1[[domain_label]]$tau2, EF_perdomain_level1[[domain_label]]$sigma2)
  pooled_pval <-mapply(p_value,EF_perdomain_level1[[domain_label]]$pval)
  pooled_qe <-EF_perdomain_level1[[domain_label]]$QE
  pooled_qedf <-EF_perdomain_level1[[domain_label]]$QEdf
  pooled_qe_p <-mapply(p_value,EF_perdomain_level1[[domain_label]]$QEp)
  pooled_qm <-EF_perdomain_level1[[domain_label]]$QM
  pooled_qmdf <-EF_perdomain_level1[[domain_label]]$QMdf
  pooled_qm_p <-mapply(p_value,EF_perdomain_level1[[domain_label]]$QMp)
  
  EF_perdomain_level1_no_rf_pooled_ef[[domain_label]]<-pooled_effect
  EF_perdomain_level1_no_rf_pooled_ci_lb[[domain_label]]<-pooled_effect_ci_lb
  EF_perdomain_level1_no_rf_pooled_ci_ub[[domain_label]]<-pooled_effect_ci_ub
  EF_perdomain_level1_no_rf_nlevel[[domain_label]]<-pooled_effect_nlevel
  EF_perdomain_level1_no_rf_I_sqr[[domain_label]]<-pooled_I2
  EF_perdomain_level1_no_rf_p[[domain_label]]<-pooled_pval
  EF_perdomain_level1_no_rf_k[[domain_label]]<-pooled_effect_k
  EF_perdomain_level1_no_rf_tau2[[domain_label]]<-pooled_effect_tau2
  EF_perdomain_level1_no_rf_qe[[domain_label]]<-pooled_qe
  EF_perdomain_level1_no_rf_qe_df[[domain_label]]<-pooled_qedf
  EF_perdomain_level1_rf_qe_p[[domain_label]]<-pooled_qe_p
  EF_perdomain_level1_rf_qm[[domain_label]]<-pooled_qm
  EF_perdomain_level1_rf_qm_df[[domain_label]]<-pooled_qmdf
  EF_perdomain_level1_rf_qm_p[[domain_label]]<-pooled_qm_p
  EF_perdomain_level1_rf_sigma2[[domain_label]]<-case_when(
    TRUE ~ sprintf("%.3f", pooled_effect_sigma2)
  )
}

# Create a data frame of pooled effects

pooled_effects_level1_perdomain_dataframe <- data.frame(

  Domain = names(EF_perdomain_level1_no_rf_pooled_ef),

  Pooled_Effect = unlist(EF_perdomain_level1_no_rf_pooled_ef),

  Pooled_cilb = unlist(EF_perdomain_level1_no_rf_pooled_ci_lb),

  Pooled_ciub  = unlist(EF_perdomain_level1_no_rf_pooled_ci_ub),
  Pooled_n=unlist(EF_perdomain_level1_no_rf_nlevel),
  Pooled_p=unlist(EF_perdomain_level1_no_rf_p),
  Pooled_k=unlist(EF_perdomain_level1_no_rf_k),
  Pooled_tau2=unlist(EF_perdomain_level1_rf_sigma2)
  
)

# Create a single forest plot to display the pooled effects of sub-domains
## reorder the table before forest plot
custom_order <-c("Simple Working Memory","Complex Working Memory","Simple Response Inhibition","Complex Response Inhibition","Response Shifting","Attention Shifting","Higher-order EF")
# Convert the 'Domain' column to a factor with the specific order
pooled_effects_level1_perdomain_dataframe <- 
  pooled_effects_level1_perdomain_dataframe[order(factor(pooled_effects_level1_perdomain_dataframe$Domain, levels = custom_order)),]

cat("less than three studies, not suitable for meta-analysis:", paste(skipped_level1_domains_lessstudyonly, collapse = ", "),"\n")

skipped_datasets_level1_perdomain <- NDDx_summary_ef_level1_and_behaviour[NDDx_summary_ef_level1_and_behaviour$Domain %in% skipped_level1_domains_lessstudyonly, ]

# View(skipped_datasets)

writexl::write_xlsx(skipped_datasets_level1_perdomain,"NDDx_control_effectsizes_EF_level1_per_domain_skippedstudies_just_removed_outliers.xlsx",col_names=TRUE)
writexl::write_xlsx(pooled_effects_level1_perdomain_dataframe,"pooled_effects_level1_perdomain_dataframe_just_removed_outliers.xlsx",col_names=TRUE)

```

## Step 2 Only Behavioural EF (No.)

```{r}
skipped_domains_norf_lessstudyonly <-c()
EF_domains<-c()
EF_domains_no_rf_pooled_ef <- list()
EF_domains_no_rf_pooled_ci_lb <- list()
EF_domains_no_rf_pooled_ci_ub <- list()
EF_domains_no_rf_nlevel <- list()
EF_domains_no_rf_I_sqr <- list()
EF_domains_no_rf_p <- list()
EF_domains_no_rf_k <- list()
EF_domains_no_rf_tau2 <- list()
EF_domains_no_rf_sigma2 <- list()
EF_domains_no_rf_qm <- list()
EF_domains_no_rf_qm_df <- list()
EF_domains_no_rf_qm_p <- list()
EF_domains_no_rf_qe <- list()
EF_domains_no_rf_qe_df <- list()
EF_domains_no_rf_qe_p <- list()

temp <-list()
flag = 1
for (domain_label in unique(NDDx_summary_ef_only_behavioural$`Domain_code`)){
  each_ef_domain_dataset <- c()
  each_ef_domain_dataset <-NDDx_summary_ef_only_behavioural%>% filter(NDDx_summary_ef_only_behavioural$`Domain_code`== domain_label)
  print(domain_label)
  if(length(unique(each_ef_domain_dataset$Study.No.)) <=2){
    skipped_domains_norf_lessstudyonly<-c(skipped_domains_norf_lessstudyonly, domain_label)
    next
  }
  #print(each_ef_domain_dataset)
  EF_domains[[flag]] <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=each_ef_domain_dataset, slab=paste(each_ef_domain_dataset$Study_year,sep=""))
  
  print(EF_domains[[flag]], digits = 3)

  
  forest_plot_efdomain<-metafor::forest(EF_domains[[flag]],addpred=TRUE,header=TRUE)
  text(x = 0, y = nrow(each_ef_domain_dataset) + 1, labels = domain_label, pos = 3) 
  # print(forest_plot_efdomain, digits = 3)
  
  # Extract pooled effect size from each domain_label
  pooled_effect <- EF_domains[[flag]]$b
  pooled_effect_ci_lb <- EF_domains[[flag]]$ci.lb
  pooled_effect_ci_ub <- EF_domains[[flag]]$ci.ub
  
  pooled_effect_nlevel <-EF_domains[[flag]]$s.nlevels # number of studies
  pooled_effect_k <-EF_domains[[flag]]$k.eff # number of outcomes
  pooled_effect_tau2 <-EF_domains[[flag]]$tau2
  pooled_effect_sigma2 <-EF_domains[[flag]]$sigma2
  pooled_I2 <- mapply(I_squared,EF_domains[[flag]]$tau2, EF_domains[[flag]]$sigma2)
  pooled_pval <-mapply(p_value,EF_domains[[flag]]$pval)
  pooled_qe <-EF_domains[[flag]]$QE
  pooled_qedf <-EF_domains[[flag]]$QEdf
  pooled_qe_p <-mapply(p_value,EF_domains[[flag]]$QEp)
  pooled_qm <-EF_domains[[flag]]$QM
  pooled_qmdf <-EF_domains[[flag]]$QMdf
  pooled_qm_p <-mapply(p_value,EF_domains[[flag]]$QMp)
  
  EF_domains_no_rf_pooled_ef[[flag]]<-pooled_effect
  EF_domains_no_rf_pooled_ci_lb[[flag]]<-pooled_effect_ci_lb
  EF_domains_no_rf_pooled_ci_ub[[flag]]<-pooled_effect_ci_ub
  EF_domains_no_rf_nlevel[[flag]]<-pooled_effect_nlevel
  EF_domains_no_rf_I_sqr[[flag]]<-pooled_I2
  EF_domains_no_rf_p[[flag]]<-pooled_pval
  EF_domains_no_rf_k[[flag]]<-pooled_effect_k
  EF_domains_no_rf_tau2[[flag]]<-pooled_effect_tau2
  EF_domains_no_rf_qe[[flag]]<-pooled_qe
  EF_domains_no_rf_qe_df[[flag]]<-pooled_qedf
  EF_domains_no_rf_qe_p[[flag]]<-pooled_qe_p
  EF_domains_no_rf_qm[[flag]]<-pooled_qm
  EF_domains_no_rf_qm_df[[flag]]<-pooled_qmdf
  EF_domains_no_rf_qm_p[[flag]]<-pooled_qm_p
  EF_domains_no_rf_sigma2[[flag]]<-case_when(
    TRUE ~ sprintf("%.3f", pooled_effect_sigma2)
  )
  
  # Create a data frame of pooled effects
  current <- data.frame(
  Domain = domain_string(domain_label),
  Pooled_Effect = unlist(EF_domains_no_rf_pooled_ef[[flag]][1]),
  Pooled_cilb = unlist(EF_domains_no_rf_pooled_ci_lb[[flag]][1]),
  Pooled_ciub  = unlist(EF_domains_no_rf_pooled_ci_ub[[flag]][1]),
  Pooled_nlevel = unlist(EF_domains_no_rf_nlevel[[flag]][1]),
  Pooled_I2= unlist(EF_domains_no_rf_I_sqr[[flag]][1]),
  Pooled_pval= unlist(EF_domains_no_rf_p[[flag]][1]),
  Pooled_k= unlist(EF_domains_no_rf_k[[flag]][1]),
  Pooled_tau2= unlist(EF_domains_no_rf_tau2[[flag]][1]),
  Pooled_sigma2= unlist(EF_domains_no_rf_sigma2[[flag]][1]),
  
  Pooled_QE= unlist(EF_domains_no_rf_qe[[flag]][1]),
  Pooled_QEdf= unlist(EF_domains_no_rf_qe_df[[flag]][1]),
  Pooled_QE_p= unlist(EF_domains_no_rf_qe_p[[flag]][1]),
  Pooled_QM= unlist(EF_domains_no_rf_qm[[flag]][1]),
  Pooled_QMdf= unlist(EF_domains_no_rf_qm_df[[flag]][1]),
  Pooled_QM_p= unlist(EF_domains_no_rf_qm_p[[flag]][1])

)
  temp[[flag]]<-current

  flag = flag +1
}

pooled_effects_efdomains_behaviour_biological_dataframe<-do.call(rbind,temp)
## reorder the table before forest plot
custom_order <-c("Simple Working Memory","Complex Working Memory","Simple Response Inhibition","Complex Response Inhibition","Response Shifting","Attention Shifting","Higher-order EF")
# Convert the 'Domain' column to a factor with the specific order
pooled_effects_efdomains_behaviour_biological_dataframe <- 
  pooled_effects_efdomains_behaviour_biological_dataframe[order(factor(pooled_effects_efdomains_behaviour_biological_dataframe$Domain, levels = custom_order)),]


setEPS()
postscript("Figure1.eps", 
           family = "Helvetica", 
           fonts = "Helvetica", 
           width = 6, height = 4, 
           pointsize = 7)
# Create a single forest plot to display the pooled effects of sub-domains
overall_forest_plot_efdomains_behaviour_biological <- metafor::forest(pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_Effect, 
                                       ci.lb = pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_cilb, 
                                       ci.ub = pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_ciub,
                                       slab = paste(pooled_effects_efdomains_behaviour_biological_dataframe$Domain),
                                       xlim = c(-15, 22),  # Adjust as needed
                                       at=c(-2, 0,2),
                                       mlab	= TRUE,
ilab=cbind(pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_k,pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_nlevel,pooled_effects_efdomains_behaviour_biological_dataframe$Pooled_pval),
                                       ilab.xpos=c(5,7,10),
                                       addsummary = TRUE,
                                       addpred=TRUE,
                                       header = "Exective Function Domain",
                                       xlab = "Hedges' g",
                                       digits = 3)

text(-5.8, c(8.4),pos=4, expression(bold("Favors NDC Group  Favors Neurotypical Group")))
text(5, c(9), expression(bold("k")))
text(7, c(9), expression(bold("n")))
text(10, c(9), expression(bold("p")))
dev.off()


# Display the overall forest plot
# print(overall_forest_plot_efdomains_behaviour_biological)

cat("less than three studies, not suitable for meta-analysis:", paste(skipped_domains_norf_lessstudyonly, collapse = ", "),"\n") 
skipped_norf_datasets <- NDDx_summary_ef_only_behavioural[NDDx_summary_ef_only_behavioural$Domain_code %in% skipped_domains_norf_lessstudyonly, ]
# writexl::write_xlsx(skipped_norf_datasets,"NDDx_control_effectsizes_EF_no_rf_perdomain_skippedstudies_just_removed_outliers.xlsx",col_names=TRUE)
writexl::write_xlsx(pooled_effects_efdomains_behaviour_biological_dataframe,"pooled_effects_efdomains_behaviour_biological_dataframe_just_removed_outliers.xlsx",col_names=TRUE)

```

## Step 4 EF domain effect (only rating form level 2)

```{r}

skipped_domains_lessstudyonly_rf_level2 <-c()
EF_domains_rf_level2<-c()
EF_domains_rf_level2_pooled_ef <- list()
EF_domains_rf_level2_pooled_ci_lb <- list()
EF_domains_rf_level2_pooled_ci_ub <- list()
temp<-list()
flag = 1
for (domain_label in unique(NDDx_summary_ef_level2$Domain_code)){
  each_ef_domain_dataset_rf_level2 <- c()
  each_ef_domain_dataset_rf_level2 <-NDDx_summary_ef_level2%>% filter(NDDx_summary_ef_level2$Domain_code== domain_label)
  #print(domain_label)
  if(length(unique(each_ef_domain_dataset_rf_level2$Study.No.)) <=2){
    skipped_domains_lessstudyonly_rf_level2<-c(skipped_domains_lessstudyonly_rf_level2, domain_label)
    next
  }
  print(domain_string(domain_label))
  EF_domains_rf_level2[[flag]] <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=each_ef_domain_dataset_rf_level2, slab=paste(each_ef_domain_dataset_rf_level2$Study.No.,sep=""))

  forest_plot_ef_rf_level2<-metafor::forest(EF_domains_rf_level2[[flag]],addpred=TRUE,header=TRUE)
  text(x = 0, y = nrow(each_ef_domain_dataset_rf_level2) + 1, labels = domain_label, pos = 3)


   # Extract pooled effect size from each domain_label
  pooled_effect <- EF_domains_rf_level2[[flag]]$b
  pooled_effect_ci_lb <- EF_domains_rf_level2[[flag]]$ci.lb
  pooled_effect_ci_ub <- EF_domains_rf_level2[[flag]]$ci.ub

  EF_domains_rf_level2_pooled_ef[[flag]]<-pooled_effect
  EF_domains_rf_level2_pooled_ci_lb[[flag]]<-pooled_effect_ci_lb
  EF_domains_rf_level2_pooled_ci_ub[[flag]]<-pooled_effect_ci_ub

  current_data <- data.frame(
  Domain = domain_string(domain_label),
  Pooled_Effect = unlist(EF_domains_rf_level2_pooled_ef[[flag]][,1]),
  Pooled_cilb = unlist(EF_domains_rf_level2_pooled_ci_lb[[flag]]),
  Pooled_ciub  = unlist(EF_domains_rf_level2_pooled_ci_ub[[flag]])

  )

  temp[[flag]]<-current_data
  flag  = flag +1

}


# Combine all data frames in the list into one data frame
pooled_effects_efdomains_ratingform_dataframe_level2 <- do.call(rbind, temp)

# Create a single forest plot to display the pooled effects of sub-domains
overall_forest_plot_efdomains_ratingform_level2 <- metafor::forest(pooled_effects_efdomains_ratingform_dataframe_level2$Pooled_Effect,
                                       ci.lb = pooled_effects_efdomains_ratingform_dataframe_level2$Pooled_cilb,
                                       ci.ub = pooled_effects_efdomains_ratingform_dataframe_level2$Pooled_ciub,
                                       slab = paste(pooled_effects_efdomains_ratingform_dataframe_level2$Domain),
                                       xlim = c(-5, 8),  # Adjust as needed
                                       addsummary = TRUE,
                                       addpred=TRUE,
                                       header = "Executive Function Rating Form Domains (Level 2)",
                                       xlab = "Hedges' g",
                                       digits = 3)


cat("less than three studies, not suitable for meta-analysis:", paste(skipped_domains_lessstudyonly_rf_level2, collapse = ", "),"\n")
skipped_datasets_rf_level2 <- NDDx_summary_ef_level2[NDDx_summary_ef_level2$Domain_code %in% skipped_domains_lessstudyonly_rf_level2, ]
# View(skipped_datasets)
writexl::write_xlsx(skipped_datasets_rf_level2,"NDDx_control_effectsizes_EF_ratingform_level2_skippedstudies_just_removed_outliers.xlsx",col_names=TRUE)

```


# -------------------------
#   - Moderator Analysis-
# -------------------------
# Intercepts: 0, denotes the average true effect/outcome when the values of all moderator variables are equal to zero.

# Moderator Analysis (Attention)

## Step 1. Age categorical


```{r}
age_moderator_categorical_attention_overall_QE<-list()
age_moderator_categorical_attention_overall_QEdf<-list()
age_moderator_categorical_attention_overall_QE_p<-list()
age_moderator_categorical_attention_overall_QM<-list()
age_moderator_categorical_attention_overall_QMdf<-list()
age_moderator_categorical_attention_overall_QM_p<-list()
age_moderator_categorical_attention_overall_I_sqr<-list()
age_moderator_categorical_attention_overall_tau2<-list()
age_moderator_categorical_attention_overall_sigma2<-list()
age_moderator_categorical_attention_overall_nlevel<-list()
age_moderator_categorical_attention_overall_k<-list()

study_info<-NDDx_summary_attention %>%
  group_by(Age.group.broader) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)
age_moderator_categorical_attention_overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`Age.group.broader`), data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study_year,sep=""))
summary(age_moderator_categorical_attention_overall, digits=3)
age_moderator_categorical_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`Age.group.broader`)-1, data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study_year,sep=""))
summary(age_moderator_categorical_attention, digits=3)


cat("individual estimate, se, zval, pval, cilb,ciub are provided, therefore not saved in xlsx","\n")
cat("however, overall results are in the excel files\n")
age_moderator_categorical_attention_overall_nlevel<-age_moderator_categorical_attention$s.nlevels
age_moderator_categorical_attention_overall_k<-age_moderator_categorical_attention$k.eff
age_moderator_categorical_attention_overall_tau2<-age_moderator_categorical_attention$tau2
age_moderator_categorical_attention_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", age_moderator_categorical_attention$sigma2)
)
age_moderator_categorical_attention_overall_I_sqr<- mapply(I_squared,age_moderator_categorical_attention$tau2, age_moderator_categorical_attention$sigma2)

age_moderator_categorical_attention_overall_QE <-age_moderator_categorical_attention$QE
age_moderator_categorical_attention_overall_QEdf <-age_moderator_categorical_attention$QEdf
age_moderator_categorical_attention_overall_QE_p <-mapply(p_value,age_moderator_categorical_attention$QEp)
age_moderator_categorical_attention_overall_QM <-age_moderator_categorical_attention$QM
age_moderator_categorical_attention_overall_QMdf <-age_moderator_categorical_attention$QMdf
age_moderator_categorical_attention_overall_QM_p <-mapply(p_value,age_moderator_categorical_attention$QMp)

age_moderator_categorical_attention_dataframe <- data.frame(

    Pooled_nlevel = age_moderator_categorical_attention_overall_nlevel,
    Pooled_I2= age_moderator_categorical_attention_overall_I_sqr,
    Pooled_k= age_moderator_categorical_attention_overall_k,
    Pooled_tau2= age_moderator_categorical_attention_overall_tau2,
    Pooled_sigma2= age_moderator_categorical_attention_overall_sigma2,

    Pooled_QE= age_moderator_categorical_attention_overall_QE,
    Pooled_QEdf= age_moderator_categorical_attention_overall_QEdf[[1]],
    Pooled_QE_p= age_moderator_categorical_attention_overall_QE_p,
    Pooled_QM= age_moderator_categorical_attention_overall_QM,
    Pooled_QMdf= age_moderator_categorical_attention_overall_QMdf[[1]],
    Pooled_QM_p= age_moderator_categorical_attention_overall_QM_p


)
# writexl::write_xlsx(age_moderator_categorical_attention_dataframe,"age_moderator_categorical_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)


es_age<-list()
cilb_age<-list()
ciub_age<-list()
current<-list()
pooled_pval<-list()
pooled_n<-list()
pooled_k<-list()

flag <-1
## Gathering individual subset data information
for (i in age_moderator_categorical_attention$btt){# "b" is a variable records factor estimates
  es_age[[i]] <-age_moderator_categorical_attention$b[i]
  cilb_age[[i]] <-age_moderator_categorical_attention$ci.lb[i]
  ciub_age[[i]] <-age_moderator_categorical_attention$ci.ub[i]
  pooled_pval[[i]] <-mapply(p_value,age_moderator_categorical_attention$pval[i])
  pooled_n[[i]]<-study_info$num_unique_studies[i]
  pooled_k[[i]]<-study_info$num_outcomes[i]

  current[[flag]] <-data.frame(
    Agegroup =age_string(i),
    Pooled_Effect = unlist(es_age[[i]]),
    Pooled_cilb = unlist(cilb_age[[i]]),
    Pooled_ciub  = unlist(ciub_age[[i]]),
    Pooled_p  = unlist(pooled_pval[[i]]),
    Pooled_n=unlist(pooled_n[[i]]),
    Pooled_k=unlist(pooled_k[[i]])

  )
  flag = flag +1
  
} 


dataframe_attention_age_overall<-do.call(rbind,current)


```
### Additional Anlaysis - Infancy group non-significant results - Need TOST test
```{r}
## note: modify equivalence boundaries based on G*power calculation
TOSTmeta(ES = 0.05, se = 0.107, low_eqbound_d=-0.2, high_eqbound_d=0.2, alpha=0.05)

```

## Step 2. Gender %male (continuous)

```{r}
gender_moderator_continuous_attention_overall_QE<-list()
gender_moderator_continuous_attention_overall_QEdf<-list()
gender_moderator_continuous_attention_overall_QE_p<-list()
gender_moderator_continuous_attention_overall_QM<-list()
gender_moderator_continuous_attention_overall_QMdf<-list()
gender_moderator_continuous_attention_overall_QM_p<-list()
gender_moderator_continuous_attention_overall_I_sqr<-list()
gender_moderator_continuous_attention_overall_tau2<-list()
gender_moderator_continuous_attention_overall_sigma2<-list()
gender_moderator_continuous_attention_overall_nlevel<-list()
gender_moderator_continuous_attention_overall_k<-list()



gender_moderator_continuous_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~`Gender....NDDx.of.Males.`, data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study.No.,sep=""))
print(gender_moderator_continuous_attention, digits=3)


gender_moderator_continuous_attention_overall_nlevel<-gender_moderator_continuous_attention$s.nlevels
gender_moderator_continuous_attention_overall_k<-gender_moderator_continuous_attention$k.eff
gender_moderator_continuous_attention_overall_tau2<-gender_moderator_continuous_attention$tau2
gender_moderator_continuous_attention_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", gender_moderator_continuous_attention$sigma2)
)
gender_moderator_continuous_attention_overall_I_sqr<- mapply(I_squared,gender_moderator_continuous_attention$tau2, gender_moderator_continuous_attention$sigma2)

gender_moderator_continuous_attention_overall_QE <-gender_moderator_continuous_attention$QE
gender_moderator_continuous_attention_overall_QEdf <-gender_moderator_continuous_attention$QEdf
gender_moderator_continuous_attention_overall_QE_p <-mapply(p_value,gender_moderator_continuous_attention$QEp)
gender_moderator_continuous_attention_overall_QM <-gender_moderator_continuous_attention$QM
gender_moderator_continuous_attention_overall_QMdf <-gender_moderator_continuous_attention$QMdf
gender_moderator_continuous_attention_overall_QM_p <-mapply(p_value,gender_moderator_continuous_attention$QMp)

gender_moderator_continuous_attention_dataframe <- data.frame(
  
    Pooled_nlevel = gender_moderator_continuous_attention_overall_nlevel,
    Pooled_I2= gender_moderator_continuous_attention_overall_I_sqr,
    Pooled_k= gender_moderator_continuous_attention_overall_k,
    Pooled_tau2= gender_moderator_continuous_attention_overall_tau2,
    Pooled_sigma2= gender_moderator_continuous_attention_overall_sigma2,
  
    Pooled_QE= gender_moderator_continuous_attention_overall_QE,
    Pooled_QEdf= gender_moderator_continuous_attention_overall_QEdf[[1]],
    Pooled_QE_p= gender_moderator_continuous_attention_overall_QE_p,
    Pooled_QM= gender_moderator_continuous_attention_overall_QM,
    Pooled_QMdf= gender_moderator_continuous_attention_overall_QMdf[[1]],
    Pooled_QM_p= gender_moderator_continuous_attention_overall_QM_p


)
# writexl::write_xlsx(gender_moderator_continuous_attention_dataframe,"gender_moderator_continuous_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```

## Step 3.NDDx diagnosis_code

```{r}
nddxdiagnosis_moderator_categoritical_attention_overall_QE<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QEdf<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QE_p<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QM<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QMdf<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QM_p<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_tau2<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_sigma2<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_nlevel<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_k<-list()


study_info<-NDDx_summary_attention %>%
  group_by(NDDx_Diagnosis_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)

nddxdiagnosis_moderator_categoritical_attention_Overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~factor(`NDDx_Diagnosis_code`), data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study.No.,sep=""))
print(nddxdiagnosis_moderator_categoritical_attention_Overall, digits=3)

nddxdiagnosis_moderator_categoritical_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~factor(`NDDx_Diagnosis_code`)-1, data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study.No.,sep=""))
print(nddxdiagnosis_moderator_categoritical_attention, digits=3)

nddxdiagnosis_moderator_categoritical_attention_overall_nlevel<-nddxdiagnosis_moderator_categoritical_attention$s.nlevels
nddxdiagnosis_moderator_categoritical_attention_overall_k<-nddxdiagnosis_moderator_categoritical_attention$k.eff
nddxdiagnosis_moderator_categoritical_attention_overall_tau2<-nddxdiagnosis_moderator_categoritical_attention$tau2
nddxdiagnosis_moderator_categoritical_attention_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", nddxdiagnosis_moderator_categoritical_attention$sigma2)
)
nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr<- mapply(I_squared,nddxdiagnosis_moderator_categoritical_attention$tau2, nddxdiagnosis_moderator_categoritical_attention$sigma2)

nddxdiagnosis_moderator_categoritical_attention_overall_QE <-nddxdiagnosis_moderator_categoritical_attention$QE
nddxdiagnosis_moderator_categoritical_attention_overall_QEdf <-nddxdiagnosis_moderator_categoritical_attention$QEdf
nddxdiagnosis_moderator_categoritical_attention_overall_QE_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_attention$QEp)
nddxdiagnosis_moderator_categoritical_attention_overall_QM <-nddxdiagnosis_moderator_categoritical_attention$QM
nddxdiagnosis_moderator_categoritical_attention_overall_QMdf <-nddxdiagnosis_moderator_categoritical_attention$QMdf
nddxdiagnosis_moderator_categoritical_attention_overall_QM_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_attention$QMp)

nddxdiagnosis_moderator_categoritical_attention_dataframe <- data.frame(
  
    Pooled_nlevel = nddxdiagnosis_moderator_categoritical_attention_overall_nlevel,
    Pooled_I2= nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr,
    Pooled_k= nddxdiagnosis_moderator_categoritical_attention_overall_k,
    Pooled_tau2= nddxdiagnosis_moderator_categoritical_attention_overall_tau2,
    Pooled_sigma2= nddxdiagnosis_moderator_categoritical_attention_overall_sigma2,
  
    Pooled_QE= nddxdiagnosis_moderator_categoritical_attention_overall_QE,
    Pooled_QEdf= nddxdiagnosis_moderator_categoritical_attention_overall_QEdf[[1]],
    Pooled_QE_p= nddxdiagnosis_moderator_categoritical_attention_overall_QE_p,
    Pooled_QM= nddxdiagnosis_moderator_categoritical_attention_overall_QM,
    Pooled_QMdf= nddxdiagnosis_moderator_categoritical_attention_overall_QMdf[[1]],
    Pooled_QM_p= nddxdiagnosis_moderator_categoritical_attention_overall_QM_p


)
# writexl::write_xlsx(nddxdiagnosis_moderator_categoritical_attention_dataframe,"nddxdiagnosis_moderator_categoritical_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)

```
## Step 3.1 NDDx diagnosis_code (N<3 NDC diagnosis code removed)

```{r}
toskip_ndc<-c()
for (ndc_code in unique(NDDx_summary_attention$NDDx_Diagnosis_code)){

  NDDx_summary_subscale_diagnosis_code_specific <- c()
  NDDx_summary_subscale_diagnosis_code_specific <-NDDx_summary_attention %>% filter(NDDx_summary_attention$NDDx_Diagnosis_code ==ndc_code)
  cat("current domain", paste(ndc_code,"study no: ",length(unique(NDDx_summary_subscale_diagnosis_code_specific$Study.No.))), collapse = ", ","\n")

  if(n_distinct(NDDx_summary_subscale_diagnosis_code_specific$Study.No.) <3){
    print("yes")
    print(ndc_code)
    toskip_ndc<-c(toskip_ndc, ndc_code)
    next
  }
}
cat("less than three studies, not suitable for meta-analysis:", paste(toskip_ndc, collapse = ", "),"\n") 

NDDx_summary_attention_morethan2<-NDDx_summary_attention[!(NDDx_summary_attention$NDDx_Diagnosis_code %in% toskip_ndc),]

nddxdiagnosis_moderator_categoritical_attention_overall_QE<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QEdf<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QE_p<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QM<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QMdf<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_QM_p<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_tau2<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_sigma2<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_nlevel<-list()
nddxdiagnosis_moderator_categoritical_attention_overall_k<-list()


study_info<-NDDx_summary_attention_morethan2 %>%
  group_by(NDDx_Diagnosis_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)

nddxdiagnosis_moderator_categoritical_attention_Overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~factor(`NDDx_Diagnosis_code`), data=NDDx_summary_attention_morethan2,
                  slab=paste(NDDx_summary_attention_morethan2$Study.No.,sep=""))
print(nddxdiagnosis_moderator_categoritical_attention_Overall, digits=3)

nddxdiagnosis_moderator_categoritical_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~factor(`NDDx_Diagnosis_code`)-1, data=NDDx_summary_attention_morethan2,
                  slab=paste(NDDx_summary_attention_morethan2$Study.No.,sep=""))
print(nddxdiagnosis_moderator_categoritical_attention, digits=3)

nddxdiagnosis_moderator_categoritical_attention_overall_nlevel<-nddxdiagnosis_moderator_categoritical_attention$s.nlevels
nddxdiagnosis_moderator_categoritical_attention_overall_k<-nddxdiagnosis_moderator_categoritical_attention$k.eff
nddxdiagnosis_moderator_categoritical_attention_overall_tau2<-nddxdiagnosis_moderator_categoritical_attention$tau2
nddxdiagnosis_moderator_categoritical_attention_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", nddxdiagnosis_moderator_categoritical_attention$sigma2)
)
nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr<- mapply(I_squared,nddxdiagnosis_moderator_categoritical_attention$tau2, nddxdiagnosis_moderator_categoritical_attention$sigma2)

nddxdiagnosis_moderator_categoritical_attention_overall_QE <-nddxdiagnosis_moderator_categoritical_attention$QE
nddxdiagnosis_moderator_categoritical_attention_overall_QEdf <-nddxdiagnosis_moderator_categoritical_attention$QEdf
nddxdiagnosis_moderator_categoritical_attention_overall_QE_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_attention$QEp)
nddxdiagnosis_moderator_categoritical_attention_overall_QM <-nddxdiagnosis_moderator_categoritical_attention$QM
nddxdiagnosis_moderator_categoritical_attention_overall_QMdf <-nddxdiagnosis_moderator_categoritical_attention$QMdf
nddxdiagnosis_moderator_categoritical_attention_overall_QM_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_attention$QMp)

nddxdiagnosis_moderator_categoritical_attention_dataframe <- data.frame(
  
    Pooled_nlevel = nddxdiagnosis_moderator_categoritical_attention_overall_nlevel,
    Pooled_I2= nddxdiagnosis_moderator_categoritical_attention_overall_I_sqr,
    Pooled_k= nddxdiagnosis_moderator_categoritical_attention_overall_k,
    Pooled_tau2= nddxdiagnosis_moderator_categoritical_attention_overall_tau2,
    Pooled_sigma2= nddxdiagnosis_moderator_categoritical_attention_overall_sigma2,
  
    Pooled_QE= nddxdiagnosis_moderator_categoritical_attention_overall_QE,
    Pooled_QEdf= nddxdiagnosis_moderator_categoritical_attention_overall_QEdf[[1]],
    Pooled_QE_p= nddxdiagnosis_moderator_categoritical_attention_overall_QE_p,
    Pooled_QM= nddxdiagnosis_moderator_categoritical_attention_overall_QM,
    Pooled_QMdf= nddxdiagnosis_moderator_categoritical_attention_overall_QMdf[[1]],
    Pooled_QM_p= nddxdiagnosis_moderator_categoritical_attention_overall_QM_p


)
# writexl::write_xlsx(nddxdiagnosis_moderator_categoritical_attention_dataframe,"nddxdiagnosis_moderator_categoritical_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```

## Step 4.Type of measure

```{r}
tom_moderator_categoritical_attention_overall_QE<-list()
tom_moderator_categoritical_attention_overall_QEdf<-list()
tom_moderator_categoritical_attention_overall_QE_p<-list()
tom_moderator_categoritical_attention_overall_QM<-list()
tom_moderator_categoritical_attention_overall_QMdf<-list()
tom_moderator_categoritical_attention_overall_QM_p<-list()
tom_moderator_categoritical_attention_overall_I_sqr<-list()
tom_moderator_categoritical_attention_overall_tau2<-list()
tom_moderator_categoritical_attention_overall_sigma2<-list()
tom_moderator_categoritical_attention_overall_nlevel<-list()
tom_moderator_categoritical_attention_overall_k<-list()


study_info<-NDDx_summary_attention %>%
  group_by(ToM_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)


tom_moderator_categoritical_attention_overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods=~factor(`ToM_code`), data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study.No.,sep=""))
print(tom_moderator_categoritical_attention_overall)
tom_moderator_categoritical_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~factor(`ToM_code`)-1, data=NDDx_summary_attention,
                  slab=paste(NDDx_summary_attention$Study.No.,sep=""))
print(tom_moderator_categoritical_attention, digits=3)

tom_moderator_categoritical_attention_overall_nlevel<-tom_moderator_categoritical_attention$s.nlevels
tom_moderator_categoritical_attention_overall_k<-tom_moderator_categoritical_attention$k.eff
tom_moderator_categoritical_attention_overall_tau2<-tom_moderator_categoritical_attention$tau2
tom_moderator_categoritical_attention_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", tom_moderator_categoritical_attention$sigma2)
)
tom_moderator_categoritical_attention_overall_I_sqr<- mapply(I_squared,tom_moderator_categoritical_attention$tau2, tom_moderator_categoritical_attention$sigma2)

tom_moderator_categoritical_attention_overall_QE <-tom_moderator_categoritical_attention$QE
tom_moderator_categoritical_attention_overall_QEdf <-tom_moderator_categoritical_attention$QEdf
tom_moderator_categoritical_attention_overall_QE_p <-mapply(p_value,tom_moderator_categoritical_attention$QEp)
tom_moderator_categoritical_attention_overall_QM <-tom_moderator_categoritical_attention$QM
tom_moderator_categoritical_attention_overall_QMdf <-tom_moderator_categoritical_attention$QMdf
tom_moderator_categoritical_attention_overall_QM_p <-mapply(p_value,tom_moderator_categoritical_attention$QMp)

tom_moderator_categoritical_attention_dataframe <- data.frame(
  
    Pooled_nlevel = tom_moderator_categoritical_attention_overall_nlevel,
    Pooled_I2= tom_moderator_categoritical_attention_overall_I_sqr,
    Pooled_k= tom_moderator_categoritical_attention_overall_k,
    Pooled_tau2= tom_moderator_categoritical_attention_overall_tau2,
    Pooled_sigma2= tom_moderator_categoritical_attention_overall_sigma2,
  
    Pooled_QE= tom_moderator_categoritical_attention_overall_QE,
    Pooled_QEdf= tom_moderator_categoritical_attention_overall_QEdf[[1]],
    Pooled_QE_p= tom_moderator_categoritical_attention_overall_QE_p,
    Pooled_QM= tom_moderator_categoritical_attention_overall_QM,
    Pooled_QMdf= tom_moderator_categoritical_attention_overall_QMdf[[1]],
    Pooled_QM_p= tom_moderator_categoritical_attention_overall_QM_p


)
# writexl::write_xlsx(tom_moderator_categoritical_attention_dataframe,"tom_moderator_categoritical_attention_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```


# --------------------------------------------
# - Moderator Analysis (EF domains) Level 1
# --------------------------------------------
## Step 1.1.1 Age categorical all studies

```{r}
age_moderator_categorical_ef_level1_and_behaviour_overall_QE<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_QEdf<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_QE_p<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_QM<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_QMdf<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_QM_p<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_I_sqr<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_tau2<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_sigma2<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_nlevel<-list()
age_moderator_categorical_ef_level1_and_behaviour_overall_k<-list()

study_info<-NDDx_summary_ef_level1_and_behaviour %>%
  group_by(Age.group.broader) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)
age_moderator_categorical_ef_level1_and_behaviour_overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, method = "REML",mods = ~factor(`Age.group.broader`), data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(age_moderator_categorical_ef_level1_and_behaviour_overall, digits=3)

age_moderator_categorical_ef_level1_and_behaviour <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, method = "REML",mods = ~factor(`Age.group.broader`)-1, data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(age_moderator_categorical_ef_level1_and_behaviour, digits=3)
cat("individual estimate, se, zval, pval, cilb,ciub are provided, therefore not saved in xlsx","\n")
cat("however, overall results are in the excel files\n")

age_moderator_categorical_ef_level1_and_behaviour_overall_nlevel<-age_moderator_categorical_ef_level1_and_behaviour$s.nlevels
age_moderator_categorical_ef_level1_and_behaviour_overall_k<-age_moderator_categorical_ef_level1_and_behaviour$k.eff
age_moderator_categorical_ef_level1_and_behaviour_overall_tau2<-age_moderator_categorical_ef_level1_and_behaviour$tau2
age_moderator_categorical_ef_level1_and_behaviour_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", age_moderator_categorical_ef_level1_and_behaviour$sigma2)
)
age_moderator_categorical_ef_level1_and_behaviour_overall_I_sqr<- mapply(I_squared,age_moderator_categorical_ef_level1_and_behaviour$tau2, age_moderator_categorical_ef_level1_and_behaviour$sigma2)

age_moderator_categorical_ef_level1_and_behaviour_overall_QE <-age_moderator_categorical_ef_level1_and_behaviour$QE
age_moderator_categorical_ef_level1_and_behaviour_overall_QEdf <-age_moderator_categorical_ef_level1_and_behaviour$QEdf
age_moderator_categorical_ef_level1_and_behaviour_overall_QE_p <-mapply(p_value,age_moderator_categorical_ef_level1_and_behaviour$QEp)
age_moderator_categorical_ef_level1_and_behaviour_overall_QM <-age_moderator_categorical_ef_level1_and_behaviour$QM
age_moderator_categorical_ef_level1_and_behaviour_overall_QMdf <-age_moderator_categorical_ef_level1_and_behaviour$QMdf
age_moderator_categorical_ef_level1_and_behaviour_overall_QM_p <-mapply(p_value,age_moderator_categorical_ef_level1_and_behaviour$QMp)

age_moderator_categorical_ef_level1_and_behaviour_dataframe <- data.frame(
  
    Pooled_nlevel = age_moderator_categorical_ef_level1_and_behaviour_overall_nlevel,
    Pooled_I2= age_moderator_categorical_ef_level1_and_behaviour_overall_I_sqr,
    Pooled_k= age_moderator_categorical_ef_level1_and_behaviour_overall_k,
    Pooled_tau2= age_moderator_categorical_ef_level1_and_behaviour_overall_tau2,
    Pooled_sigma2= age_moderator_categorical_ef_level1_and_behaviour_overall_sigma2,
  
    Pooled_QE= age_moderator_categorical_ef_level1_and_behaviour_overall_QE,
    Pooled_QEdf= age_moderator_categorical_ef_level1_and_behaviour_overall_QEdf[[1]],
    Pooled_QE_p= age_moderator_categorical_ef_level1_and_behaviour_overall_QE_p,
    Pooled_QM= age_moderator_categorical_ef_level1_and_behaviour_overall_QM,
    Pooled_QMdf= age_moderator_categorical_ef_level1_and_behaviour_overall_QMdf[[1]],
    Pooled_QM_p= age_moderator_categorical_ef_level1_and_behaviour_overall_QM_p


)
# writexl::write_xlsx(age_moderator_categorical_ef_level1_and_behaviour_dataframe,"age_moderator_categorical_ef_level1_and_behaviour_dataframe_just_removed_outliers.xlsx",col_names=TRUE)


es_age<-list()
cilb_age<-list()
ciub_age<-list()
current<-list()
pooled_pval<-list()
pooled_n<-list()
pooled_k<-list()

flag <-1
## Gathering individual subset data information
for (i in age_moderator_categorical_ef_level1_and_behaviour$btt){# "b" is a variable records factor estimates
  es_age[[i]] <-age_moderator_categorical_ef_level1_and_behaviour$b[i]
  cilb_age[[i]] <-age_moderator_categorical_ef_level1_and_behaviour$ci.lb[i]
  ciub_age[[i]] <-age_moderator_categorical_ef_level1_and_behaviour$ci.ub[i]
  pooled_pval[[i]] <-mapply(p_value,age_moderator_categorical_ef_level1_and_behaviour$pval[i])
  pooled_n[[i]]<-study_info$num_unique_studies[i]
  pooled_k[[i]]<-study_info$num_outcomes[i]

  current[[flag]] <-data.frame(
    Agegroup =age_string(i),
    Pooled_Effect = unlist(es_age[[i]]),
    Pooled_cilb = unlist(cilb_age[[i]]),
    Pooled_ciub  = unlist(ciub_age[[i]]),
    Pooled_p  = unlist(pooled_pval[[i]]),
    Pooled_n=unlist(pooled_n[[i]]),
    Pooled_k=unlist(pooled_k[[i]])

  )
  flag = flag +1
  
} 
dataframe_overall_ef_level1_and_behaviour_age<-do.call(rbind,current)
```

## Plotting Figure2
```{r}

# Convert dimensions from millimeters to inches
width_mm <- 180  # width in millimeters
height_mm <- 210 # height in millimeters

width_in <- width_mm / 25.4  # Convert to inches
height_in <- height_mm / 25.4 # Convert to inches
# setEPS()
postscript("Forestplots_Figure2.eps", width = width_in, height = height_in, family = "Helvetica")

par(mfrow = c(2, 1), mar = c(5, 4, 4, 2) + 0.1, oma = c(3, 1, 3, 1), 
    family = "Helvetica", cex = 0.7, cex.lab = 0.7, cex.axis = 0.7, cex.main = 0.8)
# Create a single forest plot to display the pooled effects of sub-domains
overall_forest_plot_attention_age <- metafor::forest(dataframe_attention_age_overall$Pooled_Effect,
                                       ci.lb = dataframe_attention_age_overall$Pooled_cilb,
                                       ci.ub = dataframe_attention_age_overall$Pooled_ciub,
                                       slab = paste(dataframe_attention_age_overall$Agegroup),
                                       ilab=cbind(dataframe_attention_age_overall$Pooled_k,dataframe_attention_age_overall$Pooled_n,dataframe_attention_age_overall$Pooled_p),
                                       ilab.xpos=c(5,7,10),
                                       at=c(-2,0,2),
                                       xlim = c(-15, 22),  # Adjust as needed
                                       # addsummary = TRUE,
                                       # addpred=TRUE,
                                       header = "Age group",
                                       xlab = "Hedges' g",
                                       digits = 3)
text(-9, c(4.2),pos=4, expression(bold("Favors NDC Group  Favors Neurotypical Group")))
text(5, c(5), expression(bold("k")))
text(7, c(5), expression(bold("n")))
text(10, c(5), expression(bold("p")))
text(0, c(5.5),pos=4, expression(bold("Attention")))
mtext("(A)", side = 1, line = 5, at = mean(par("usr")[1:2]), cex = 0.7, family = "Helvetica")


# Create a single forest plot to display the pooled effects of sub-domains
overall_forest_plot_EF_level1_age <- metafor::forest(dataframe_overall_ef_level1_and_behaviour_age$Pooled_Effect,
                                       ci.lb = dataframe_overall_ef_level1_and_behaviour_age$Pooled_cilb,
                                       ci.ub = dataframe_overall_ef_level1_and_behaviour_age$Pooled_ciub,
                                       slab = paste(dataframe_overall_ef_level1_and_behaviour_age$Agegroup),
                                       xlim = c(-15, 22),  # Adjust as needed
                                       at = c(-2,0,2),
                                      mlab	= TRUE,
ilab= cbind(dataframe_overall_ef_level1_and_behaviour_age$Pooled_k,dataframe_overall_ef_level1_and_behaviour_age$Pooled_n,dataframe_overall_ef_level1_and_behaviour_age$Pooled_p),
                                       ilab.xpos=c(5,7,10),
                                       # addsummary = TRUE,
                                       # addpred=TRUE,
                                       header = "Age group",
                                       xlab = "Hedges' g",
                                       digits = 3)
text(0, c(5.5),pos=4, expression(bold("Executive Function")))
text(-9, c(4.2),pos=4, expression(bold("Favors NDC Group  Favors Neurotypical Group")))
text(5, c(5), expression(bold("k")))
text(7, c(5), expression(bold("n")))
text(10, c(5), expression(bold("p")))
mtext("(B)", side = 1, line = 5, at = mean(par("usr")[1:2]), cex = 0.7, family = "Helvetica")

dev.off()
```
### Additional analysis on equivlance test
```{r}
## note: modify equivalence boundaries based on G*power calculation
TOSTmeta(ES = -0.444, se = 0.346, low_eqbound_d=-0.2, high_eqbound_d=0.2, alpha=0.05)
```

## Step 2. Gender %male (continuous) overall EF effect

```{r}


gender_moderator_continuous_ef_level1_and_behaviour_overall_QE<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_QEdf<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_QE_p<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_QM<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_QMdf<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_QM_p<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_I_sqr<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_tau2<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_sigma2<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_nlevel<-list()
gender_moderator_continuous_ef_level1_and_behaviour_overall_k<-list()
gender_moderator_continuous_ef_level1_and_behaviour <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods =~ `Gender....NDDx.of.Males.`, data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(gender_moderator_continuous_ef_level1_and_behaviour, digits=3)

gender_moderator_continuous_ef_level1_and_behaviour_overall_nlevel<-gender_moderator_continuous_ef_level1_and_behaviour$s.nlevels
gender_moderator_continuous_ef_level1_and_behaviour_overall_k<-gender_moderator_continuous_ef_level1_and_behaviour$k.eff
gender_moderator_continuous_ef_level1_and_behaviour_overall_tau2<-gender_moderator_continuous_ef_level1_and_behaviour$tau2
gender_moderator_continuous_ef_level1_and_behaviour_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", gender_moderator_continuous_ef_level1_and_behaviour$sigma2)
)
gender_moderator_continuous_ef_level1_and_behaviour_overall_I_sqr<- mapply(I_squared,gender_moderator_continuous_ef_level1_and_behaviour$tau2, gender_moderator_continuous_ef_level1_and_behaviour$sigma2)

gender_moderator_continuous_ef_level1_and_behaviour_overall_QE <-gender_moderator_continuous_ef_level1_and_behaviour$QE
gender_moderator_continuous_ef_level1_and_behaviour_overall_QEdf <-gender_moderator_continuous_ef_level1_and_behaviour$QEdf
gender_moderator_continuous_ef_level1_and_behaviour_overall_QE_p <-mapply(p_value,gender_moderator_continuous_ef_level1_and_behaviour$QEp)
gender_moderator_continuous_ef_level1_and_behaviour_overall_QM <-gender_moderator_continuous_ef_level1_and_behaviour$QM
gender_moderator_continuous_ef_level1_and_behaviour_overall_QMdf <-gender_moderator_continuous_ef_level1_and_behaviour$QMdf
gender_moderator_continuous_ef_level1_and_behaviour_overall_QM_p <-mapply(p_value,gender_moderator_continuous_ef_level1_and_behaviour$QMp)

gender_moderator_continuous_ef_level1_and_behaviour_dataframe <- data.frame(
  
    Pooled_nlevel = gender_moderator_continuous_ef_level1_and_behaviour_overall_nlevel,
    Pooled_I2= gender_moderator_continuous_ef_level1_and_behaviour_overall_I_sqr,
    Pooled_k= gender_moderator_continuous_ef_level1_and_behaviour_overall_k,
    Pooled_tau2= gender_moderator_continuous_ef_level1_and_behaviour_overall_tau2,
    Pooled_sigma2= gender_moderator_continuous_ef_level1_and_behaviour_overall_sigma2,
  
    Pooled_QE= gender_moderator_continuous_ef_level1_and_behaviour_overall_QE,
    Pooled_QEdf= gender_moderator_continuous_ef_level1_and_behaviour_overall_QEdf[[1]],
    Pooled_QE_p= gender_moderator_continuous_ef_level1_and_behaviour_overall_QE_p,
    Pooled_QM= gender_moderator_continuous_ef_level1_and_behaviour_overall_QM,
    Pooled_QMdf= gender_moderator_continuous_ef_level1_and_behaviour_overall_QMdf[[1]],
    Pooled_QM_p= gender_moderator_continuous_ef_level1_and_behaviour_overall_QM_p


)
# writexl::write_xlsx(gender_moderator_continuous_ef_level1_and_behaviour_dataframe,"gender_moderator_continuous_ef_level1_and_behaviour_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```

## Step 3.NDDxx diagnosis_code Overall Effect

```{r}
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k<-list()

study_info<-NDDx_summary_ef_level1_and_behaviour %>%
  group_by(NDDx_Diagnosis_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`NDDx_Diagnosis_code`), data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall, digits=3)


nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`NDDx_Diagnosis_code`)-1, data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour, digits=3)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$s.nlevels
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$k.eff
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$tau2
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$sigma2)
)
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<- mapply(I_squared,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$tau2, nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$sigma2)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QE
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QEdf
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QEp)
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QM
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QMdf
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QMp)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe <- data.frame(
  
    Pooled_nlevel = nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel,
    Pooled_I2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr,
    Pooled_k= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k,
    Pooled_tau2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2,
    Pooled_sigma2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2,
  
    Pooled_QE= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE,
    Pooled_QEdf= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf[[1]],
    Pooled_QE_p= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p,
    Pooled_QM= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM,
    Pooled_QMdf= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf[[1]],
    Pooled_QM_p= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p


)
# writexl::write_xlsx(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe,"nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe_just_removed_outliers.xlsx",col_names=TRUE)

```
## Step 3.1 NDDxx diagnosis_code Overall Effect (N<3 NDC diagnosis code removed)

```{r}
toskip_ndc<-c()
for (ndc_code in unique(NDDx_summary_ef_level1_and_behaviour$NDDx_Diagnosis_code)){

  NDDx_summary_subscale_diagnosis_code_specific <- c()
  NDDx_summary_subscale_diagnosis_code_specific <-NDDx_summary_ef_level1_and_behaviour %>% filter(NDDx_summary_ef_level1_and_behaviour$NDDx_Diagnosis_code ==ndc_code)
  cat("current domain", paste(ndc_code,"study no: ",length(unique(NDDx_summary_subscale_diagnosis_code_specific$Study.No.))), collapse = ", ","\n")

  if(n_distinct(NDDx_summary_subscale_diagnosis_code_specific$Study.No.) <3){
    print("yes")
    print(ndc_code)
    toskip_ndc<-c(toskip_ndc, ndc_code)
    next
  }
}
cat("less than three studies, not suitable for meta-analysis:", paste(toskip_ndc, collapse = ", "),"\n") 

NDDx_summary_ef_level1_and_behaviour_morethan2<-NDDx_summary_ef_level1_and_behaviour[!(NDDx_summary_ef_level1_and_behaviour$NDDx_Diagnosis_code %in% toskip_ndc),]


nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-list()
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k<-list()

study_info<-NDDx_summary_ef_level1_and_behaviour_morethan2 %>%
  group_by(NDDx_Diagnosis_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`NDDx_Diagnosis_code`), data=NDDx_summary_ef_level1_and_behaviour_morethan2,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour_morethan2$Study.No.,sep=""))
summary(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall, digits=3)


nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`NDDx_Diagnosis_code`)-1, data=NDDx_summary_ef_level1_and_behaviour_morethan2,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour_morethan2$Study.No.,sep=""))
summary(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour, digits=3)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$s.nlevels
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$k.eff
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$tau2
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$sigma2)
)
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<- mapply(I_squared,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$tau2, nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$sigma2)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QE
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QEdf
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QEp)
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QM
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf <-nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QMdf
nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p <-mapply(p_value,nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour$QMp)

nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe <- data.frame(
  
    Pooled_nlevel = nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel,
    Pooled_I2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr,
    Pooled_k= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_k,
    Pooled_tau2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_tau2,
    Pooled_sigma2= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2,
  
    Pooled_QE= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE,
    Pooled_QEdf= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf[[1]],
    Pooled_QE_p= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p,
    Pooled_QM= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM,
    Pooled_QMdf= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf[[1]],
    Pooled_QM_p= nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p


)
# writexl::write_xlsx(nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe,"nddxdiagnosis_moderator_categoritical_ef_level1_and_behaviour_dataframe_just_removed_outliers.xlsx",col_names=TRUE)

```



## Step 4.Type of measure moderator Overall Effect

```{r}

study_info<-NDDx_summary_ef_level1_and_behaviour %>%
  group_by(ToM_code) %>%
  summarise(
  num_unique_studies = n_distinct(Study.No.),
  num_outcomes = n()
)
print(study_info)
tom_moderator_categoritical_ef_level1_and_behaviour_overall<- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`ToM_code`), data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
print(tom_moderator_categoritical_ef_level1_and_behaviour_overall, digits=3)

tom_moderator_categoritical_ef_level1_and_behaviour<- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`ToM_code`)-1, data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
print(tom_moderator_categoritical_ef_level1_and_behaviour, digits=3)

tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-list()
tom_moderator_categoritical_ef_level1_and_behaviour_overall_k<-list()
tom_moderator_categoritical_ef_level1_and_behaviour<- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, mods = ~factor(`ToM_code`)-1, data=NDDx_summary_ef_level1_and_behaviour,
                  slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(tom_moderator_categoritical_ef_level1_and_behaviour, digits=3)

tom_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel<-tom_moderator_categoritical_ef_level1_and_behaviour$s.nlevels
tom_moderator_categoritical_ef_level1_and_behaviour_overall_k<-tom_moderator_categoritical_ef_level1_and_behaviour$k.eff
tom_moderator_categoritical_ef_level1_and_behaviour_overall_tau2<-tom_moderator_categoritical_ef_level1_and_behaviour$tau2
tom_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2<-case_when(
    TRUE ~ sprintf("%.3f", tom_moderator_categoritical_ef_level1_and_behaviour$sigma2)
)
tom_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr<- mapply(I_squared,tom_moderator_categoritical_ef_level1_and_behaviour$tau2, tom_moderator_categoritical_ef_level1_and_behaviour$sigma2)

tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE <-tom_moderator_categoritical_ef_level1_and_behaviour$QE
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf <-tom_moderator_categoritical_ef_level1_and_behaviour$QEdf
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p <-mapply(p_value,tom_moderator_categoritical_ef_level1_and_behaviour$QEp)
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM <-tom_moderator_categoritical_ef_level1_and_behaviour$QM
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf <-tom_moderator_categoritical_ef_level1_and_behaviour$QMdf
tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p <-mapply(p_value,tom_moderator_categoritical_ef_level1_and_behaviour$QMp)

tom_moderator_categoritical_ef_level1_and_behaviour_dataframe <- data.frame(
  
    Pooled_nlevel = tom_moderator_categoritical_ef_level1_and_behaviour_overall_nlevel,
    Pooled_I2= tom_moderator_categoritical_ef_level1_and_behaviour_overall_I_sqr,
    Pooled_k= tom_moderator_categoritical_ef_level1_and_behaviour_overall_k,
    Pooled_tau2= tom_moderator_categoritical_ef_level1_and_behaviour_overall_tau2,
    Pooled_sigma2= tom_moderator_categoritical_ef_level1_and_behaviour_overall_sigma2,
  
    Pooled_QE= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE,
    Pooled_QEdf= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QEdf[[1]],
    Pooled_QE_p= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QE_p,
    Pooled_QM= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM,
    Pooled_QMdf= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QMdf[[1]],
    Pooled_QM_p= tom_moderator_categoritical_ef_level1_and_behaviour_overall_QM_p


)
# writexl::write_xlsx(tom_moderator_categoritical_ef_level1_and_behaviour_dataframe,"tom_moderator_categoritical_ef_level1_and_behaviour_dataframe_just_removed_outliers.xlsx",col_names=TRUE)
```

#----------------------------
# - Remove high-risk group
#----------------------------
```{r}
## Comparing to manual inspection excel sheet, remove data if column "remove" is 1.
# #remove due to less than 3 subgroups.
manual_remove_dataframe <- read_excel("NDDx_control_effectsizes_lessthan3subgroupsremoved.xlsx")
filtered_all_NDDx_control <- filtered_all_NDDx_control[manual_remove_dataframe$Remove==0,]
# remove highrisks before analysis
highrisk_code <-c("11","14","15","16","17")
filtered_all_NDDx_control <- filtered_all_NDDx_control[!(filtered_all_NDDx_control$NDDx_Diagnosis_code %in% highrisk_code), ]
NDDx_summary <- escalc(yi=yi,vi=vi,data=filtered_all_NDDx_control)
NDDx_summary_ef <-NDDx_summary%>% filter(NDDx_summary$EF_Attention == "executive function")

## level 1 (sub-scales are not included for the overall study effects)

ef_level1<-c("global executive function","effortful control")
# NDDx_summary_ef_behaviour_biological_global_effortforcontrol <- NDDx_summary_ef[(NDDx_summary_ef$`Domain (e.g., sustained attention, selective attention, working memory, response inhibition etc)` %in% ef_level1), ] 

# Behavioural is study all to be included, for rating form (only global executive function and eefortful control are included in all future analysis) -EF studies
strings_to_match <- c( "behavioural","Behavioural")
strings_rf <- c( "rating form")

NDDx_summary_ef_only_behavioural <- NDDx_summary_ef[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary_ef$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE), ]

NDDx_summary_ef_level1_and_behaviour <- NDDx_summary_ef[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary_ef$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE) |
  NDDx_summary_ef$`Domain` %in% ef_level1,]

NDDx_summary_ef_level1_and_behaviour_attention_combined <- NDDx_summary[
  grepl(paste(strings_to_match, collapse = "|"), NDDx_summary$Type.of.measure..i.e...biological..behavioural..rating.form., ignore.case = TRUE) |
  NDDx_summary$`Domain` %in% ef_level1,]
#level 2 means all subscales (not global and effortforcontrol) in rating form only EF Studies
# NDDx_summary_ef_exclude_global_effortforcontrol <- NDDx_summary_ef_ratingform[!(NDDx_summary_ef_ratingform$`Domain` %in% ef_level1), ] 


NDDx_summary_ef_ratingform<-NDDx_summary_ef[(NDDx_summary_ef$`Type.of.measure..i.e...biological..behavioural..rating.form.` %in% strings_rf),]
NDDx_summary_ef_ratingform_level1<-NDDx_summary_ef_level1_and_behaviour[(NDDx_summary_ef_level1_and_behaviour$`Type.of.measure..i.e...biological..behavioural..rating.form.` %in% strings_rf),]

NDDx_summary_ef_level2 <- NDDx_summary_ef_ratingform[!(NDDx_summary_ef_ratingform$`Domain` %in% ef_level1),]

domain_subscales <-c(7,8,9,10,11)
NDDx_summary_ef_ratingform_subscales <-  NDDx_summary_ef_ratingform[NDDx_summary_ef_ratingform$Domain_code %in% domain_subscales, ] # domains 7-11
domain_factors <-c(12,13,14)
NDDx_summary_ef_ratingform_factors <-  NDDx_summary_ef_ratingform[NDDx_summary_ef_ratingform$Domain_code %in% domain_factors, ] # domains 7-11


NDDx_summary_attention <-NDDx_summary%>% filter(NDDx_summary$EF_Attention == "attention")
writexl::write_xlsx(NDDx_summary_ef,"NDDx_control_effectsizes_executivefunction_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_level1_and_behaviour,"NDDx_control_effectsizes_executivefunction_global_effortfor_behavioural_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_level2,"NDDx_control_effectsizes_executivefunction_subscales_inratingform_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_attention,"NDDx_control_effectsizes_attention_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_only_behavioural,"NDDx_control_effectsizes_onlybehaviour_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_ratingform_level1,"NDDx_control_effectsizes_onlyrf_level1_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_level1_and_behaviour_attention_combined,"NDDx_control_effectsizes_attention_and_ef_level1_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_ratingform_subscales,"NDDx_control_effectsizes_ef_ratingform_subscales_remove_outlierandhighriskversion.xlsx",col_names=TRUE)
writexl::write_xlsx(NDDx_summary_ef_ratingform_factors,"NDDx_control_effectsizes_ef_ratingform_factors_remove_outlierandhighriskversion.xlsx",col_names=TRUE)

# View(NDDx_summary_ef)
# NDDx_summary_ef[, 1] <- as.numeric(as.character(NDDx_summary_ef[, 1]))
# NDDx_summary_ef[, 6] <- as.numeric(as.character(NDDx_summary_ef[, 6]))
NDDx_summary_ef_level1_and_behaviour[, 1] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour[, 1]))
NDDx_summary_ef_level1_and_behaviour[, 6] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour[, 6]))
NDDx_summary_ef_ratingform_level1[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_level1[, 1]))
NDDx_summary_ef_ratingform_level1[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_level1[, 6]))
NDDx_summary_ef_level2[, 1] <- as.numeric(as.character(NDDx_summary_ef_level2[, 1]))
NDDx_summary_ef_level2[, 6] <- as.numeric(as.character(NDDx_summary_ef_level2[, 6]))
# View(NDDx_summary_attention)
NDDx_summary_attention[, 1] <- as.numeric(as.character(NDDx_summary_attention[, 1]))
NDDx_summary_attention[, 6] <- as.numeric(as.character(NDDx_summary_attention[, 6]))
NDDx_summary_ef_only_behavioural[, 1] <- as.numeric(as.character(NDDx_summary_ef_only_behavioural[, 1]))
NDDx_summary_ef_only_behavioural[, 6] <- as.numeric(as.character(NDDx_summary_ef_only_behavioural[, 6]))
NDDx_summary_ef_level1_and_behaviour_attention_combined[, 1] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour_attention_combined[, 1]))
NDDx_summary_ef_level1_and_behaviour_attention_combined[, 6] <- as.numeric(as.character(NDDx_summary_ef_level1_and_behaviour_attention_combined[, 6]))
NDDx_summary_ef_ratingform_subscales[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_subscales[, 1]))
NDDx_summary_ef_ratingform_subscales[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_subscales[, 6]))
NDDx_summary_ef_ratingform_factors[, 1] <- as.numeric(as.character(NDDx_summary_ef_ratingform_factors[, 1]))
NDDx_summary_ef_ratingform_factors[, 6] <- as.numeric(as.character(NDDx_summary_ef_ratingform_factors[, 6]))


```
## Step 2.1: overall random effect (EF level 1 and behaviour)

```{r}
# Multi-variant random effect (across studies) executive 
current<-list()
random_effect_study_ef_level1 <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$Study.No.,sep=""))
summary(random_effect_study_ef_level1, digits=3)
predict(random_effect_study_ef_level1)
pooled_effect <- random_effect_study_ef_level1$b
pooled_effect_ci_lb <- random_effect_study_ef_level1$ci.lb
pooled_effect_ci_ub <- random_effect_study_ef_level1$ci.ub
  
pooled_effect_nlevel <-random_effect_study_ef_level1$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_ef_level1$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_ef_level1$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_ef_level1$tau2, random_effect_study_ef_level1$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_ef_level1$pval)
pooled_qe <-random_effect_study_ef_level1$QE
pooled_qedf <-random_effect_study_ef_level1$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_ef_level1$QEp)
pooled_qm <-random_effect_study_ef_level1$QM
pooled_qmdf <-random_effect_study_ef_level1$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_ef_level1$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  # Pooled_sigma2= unlist(pooled_effect_sigma2),
  
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
forest(random_effect_study_ef_level1)

writexl::write_xlsx(current,"pooled_overall_ef_level1_behaviour_outlierandhighriskremoved.xlsx",col_names=TRUE)
```
### Step 2.1.1: Funnel plot and trim-and-fill analysis (EF level 1 and behaviour)
```{r}
NDDx_summary_ef_level1_and_behaviour$SE<-sqrt(NDDx_summary_ef_level1_and_behaviour$vi)
Data_meta_means_NDDx_summary_ef_level1_and_behaviour <-
  NDDx_summary_ef_level1_and_behaviour %>% select(`Study.No.`, `Domain`, yi, SE, vi) %>%
  group_by(`Study.No.`,) %>%
  summarise(mean_g=mean(yi),mean_SE=mean(SE), mean_Vi=mean(vi))

eggers_EF <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_ef_level1_and_behaviour,slab=paste(NDDx_summary_ef_level1_and_behaviour$`Study.No.`,sep=""))
## Uni-variant 
random_effect_study_ef_level1_and_behaviour_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_ef_level1_and_behaviour) 
print(random_effect_study_ef_level1_and_behaviour_univariant,digits=3)
predict(random_effect_study_ef_level1_and_behaviour_univariant)
funnel(random_effect_study_ef_level1_and_behaviour_univariant)

taf_ef_level1 <- trimfill(random_effect_study_ef_level1_and_behaviour_univariant, side = "left")
funnel(taf_ef_level1)
```

## Step 2.2: overall random effect (Attention)

```{r}
#Multi-variant random effect (across studies) attention
current<-list()
random_effect_study_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$Study.No.,sep=""))
summary(random_effect_study_attention, digits=3)
predict(random_effect_study_attention)
pooled_effect <- random_effect_study_attention$b
pooled_effect_ci_lb <- random_effect_study_attention$ci.lb
pooled_effect_ci_ub <- random_effect_study_attention$ci.ub
  
pooled_effect_nlevel <-random_effect_study_attention$s.nlevels # number of studies
pooled_effect_k <-random_effect_study_attention$k.eff # number of outcomes
pooled_effect_tau2 <-case_when(
                                  TRUE ~sprintf("%.3f",random_effect_study_attention$sigma2)
                      )
pooled_I2 <- mapply(I_squared,random_effect_study_attention$tau2, random_effect_study_attention$sigma2)
pooled_pval <-mapply(p_value,random_effect_study_attention$pval)
pooled_qe <-random_effect_study_attention$QE
pooled_qedf <-random_effect_study_attention$QEdf
pooled_qe_p <-mapply(p_value,random_effect_study_attention$QEp)
pooled_qm <-random_effect_study_attention$QM
pooled_qmdf <-random_effect_study_attention$QMdf[1]
pooled_qm_p <-mapply(p_value,random_effect_study_attention$QMp)

  # Create a data frame of pooled effects
current <- data.frame(
  Pooled_Effect = unlist(pooled_effect),
  Pooled_cilb = unlist(pooled_effect_ci_lb),
  Pooled_ciub  = unlist(pooled_effect_ci_ub),
  Pooled_nlevel = unlist(pooled_effect_nlevel),
  Pooled_I2= unlist(pooled_I2),
  Pooled_pval= unlist(pooled_pval),
  Pooled_k= unlist(pooled_effect_k),
  Pooled_tau2= unlist(pooled_effect_tau2),
  
  Pooled_QE= unlist(pooled_qe),
  Pooled_QEdf= unlist(pooled_qedf),
  Pooled_QE_p= unlist(pooled_qe_p),
  Pooled_QM= unlist(pooled_qm),
  Pooled_QMdf= unlist(pooled_qmdf),
  Pooled_QM_p= unlist(pooled_qm_p)

)
forest(random_effect_study_attention)
writexl::write_xlsx(current,"pooled_overall_attention_outlierandhighriskremoved.xlsx",col_names=TRUE)
```

### Step 2.2.1: Funnel plot and trim-and-fill analysis (Attention)
```{r}
NDDx_summary_attention$SE<-sqrt(NDDx_summary_attention$vi)
Data_meta_means_NDDx_summary_attention <-
  NDDx_summary_attention %>% select(`Study.No.`, `Domain`, yi, SE, vi) %>%
  group_by(`Study.No.`,) %>%
  summarise(mean_g=mean(yi),mean_SE=mean(SE), mean_Vi=mean(vi))

eggers_attention <- rma.mv(yi, vi, random = ~ 1 |`Study.No.`,mods = SE, data=NDDx_summary_attention,slab=paste(NDDx_summary_attention$`Study.No.`,sep=""))
## Uni-variant 
random_effect_study_attention_univariant <- rma(yi = mean_g, sei = mean_SE, data =Data_meta_means_NDDx_summary_attention) 
print(random_effect_study_attention_univariant,digits=3)
predict(random_effect_study_attention_univariant)
funnel(random_effect_study_attention_univariant)

taf_attention <- trimfill(random_effect_study_attention_univariant, side = "left")
funnel(taf_attention)
```